---
title: "Comparative Cognition Numerosity Analysis of Cowlog data Part II"
author: "Kelly Wallace"
date: "March 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document takes the output from "Comparative Cognition Numerosity Cowlog Analysis.Rmd" and graphs relevant data. 
Note: Comparative Cognition Numerosity Cowlog Analysis.Rmd takes all the individual cowlog score sheets for numerosity and summarized them into one datasheet, df.sum

Individuals in the data output from the first rmd: 
wahida, wheatley,winnifred, wisteria,wayne, gabi,wile, wyatt,wedelia, gavin,gretchen, wade,willis, gloria,waldhurga, garrison,george, waverly,wilbur, wildflower,gemma, gertrude,grayson, watson,gary, winter,georgiafixed, wendy,gladys, gibson,gina, griffin,gabriel, winona,gideon,gordon, 

ORDER OF ANALYSIS:
1. Pairwise comparisons of the following (one value per individual) performance metrics:
Average performance over full 4 minutes
Average performance over T30 to T50
Proportion of correct first choices
Average latency to approach correct side
Mean of median perofomance on each ratio
number of medians above 0.60 using full 4 minutes data
number of medians above 0.60 using full 4 minutes data


2. Pairwise comparison of the performance metrics (one value per individual) to the following behavior metrics:
Average number of entries
Average reaction time

3. Investigating other factors (compare performance to):
sex, 
size, 
order,

4. See how consistent individuals are across trials within the same individuals (so will have an average repeatibility score?)
Performance over the full 4 minutes
Performance over T30 to T50
Which side was chosen first



```{r}
library(ggplot2)
library(dplyr)
library(rmarkdown)
library(knitr)
library(readr)
library(utils)


df<- read_csv("C:/Users/Kelly/Desktop/Grad School/Cummings Lab/Comparative Cognition/Numerosity Comparative Cognition Full Dataset March_19_2018.csv", col_names = TRUE, col_types = NULL)

View(df)


#TEMPLATE---------

p <- ggplot(df, aes(XXX, XXX))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = 0.007277, R-squared:  0.1987
        ", size = 6, color = "black") + 
  labs(x= "XXX",y="XXX") +
  ggtitle ("Note:XXX") +
  geom_smooth(method = "lm")

mod<- lm(df$XXX ~ df$XXX, na.rm = TRUE)
summary(mod)



```


```{r}
#Does average performance over just T30 to T50 predict average performance over the full 4 minutes?

p <- ggplot(df, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = 0.007277, R-squared:  0.1987
        ", size = 6, color = "black") + 
  labs(x= "average_performance_across_all_9_testing_trials_using_T30_to_T50_data",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Note:Does average performance over just T30 to T50 predict 
           average performance over the full 4 minutes?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data, na.rm = TRUE)
summary(mod)

```



```{r}

#Does proportion of correct first choices predict average performance (T30 to T50 data)?
p <- ggplot(df, aes(proportion_of_correct_first_choices, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.63, label= "p = 0.01904, R-squared: 0.1556
        ", size = 6, color = "black") + 
  labs(x= "proportion_of_correct_first_choices",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Note:Does proportion of correct first 
           choices predict average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$proportion_of_correct_first_choices, na.rm = TRUE)
summary(mod)


```

```{r}
#Does proportion of correct first choices predict average performance (full four minutes data)?
p <- ggplot(df, aes(proportion_of_correct_first_choices, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = 0.8697, R-squared:  0.0008276
        ", size = 6, color = "black") + 
  labs(x= "proportion_of_correct_first_choices",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Note:Does proportion of correct first choices 
           predict average performance (full four minutes data)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$proportion_of_correct_first_choices, na.rm = TRUE)
summary(mod)
```

```{r}

#Does average latency to enter the correct side predict proportion of first choices (speed accuracy tradeoff)?
p <- ggplot(df, aes(average_latency_to_enter_correct_side, proportion_of_correct_first_choices))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=30, y=0.8, label= "p = 0.08298, R-squared:  0.08831
        ", size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does average latency to enter the correct side predict 
           proportion of first choices (speed accuracy tradeoff)?") +
  geom_smooth(method = "lm")

mod<- lm(df$proportion_of_correct_first_choices ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)
```

```{r}
#Does average latency to enter the correct side predict average performance over full 4 minutes data (speed accuracy tradeoff)?
p <- ggplot(df, aes(average_latency_to_enter_correct_side, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= "p = 0.01221, R-squared:  0.1757
        ", size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Note:Does average latency to enter the correct side predict 
           average performance over full 4 minutes data (speed accuracy tradeoff)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)
```

```{r}
#Does average latency to enter correct side predict average performance (T30 to T50 data)?
p <- ggplot(df, aes(average_latency_to_enter_correct_side, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= "p = 0.0003672, R-squared:  0.3231
        ", size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Note:Does average latency to enter correct side predict 
           average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)
```


```{r}
#Does Mean of median performance on each ratio (T30 to T50 data) predict proportion of correct first choices?
p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_T30_to_T50_data, proportion_of_correct_first_choices))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = 0.09966, R-squared: 0.08778
        ", size = 6, color = "black") + 
  labs(x= "mean_of_median_performance_on_each_ratio_T30_to_T50_data",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does Mean of median performance on each ratio 
           (T30 to T50 data) predict proportion of correct first choices?") +
  geom_smooth(method = "lm")

mod<- lm(df$proportion_of_correct_first_choices ~ df$mean_of_median_performance_on_each_ratio_T30_to_T50_data, na.rm = TRUE)
summary(mod)
```



```{r}
#Does Mean of median performance on each ratio (full 4 minutes) predict proportion of correct first choices?
p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_full_four_minutes_data, proportion_of_correct_first_choices))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = 0.5818, R-squared: 0.009582
        ", size = 6, color = "black") + 
  labs(x= "mean_of_median_performance_on_each_ratio_full_four_minutes_data",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does Mean of median performance on each ratio 
           (full 4 minutes) predict proportion of correct first choices?") +
  geom_smooth(method = "lm")

mod<- lm(df$proportion_of_correct_first_choices ~ df$mean_of_median_performance_on_each_ratio_full_four_minutes_data, na.rm = TRUE)
summary(mod)
```



```{r}
#Does average latency to enter correct side predict mean of median performance on each ratio (mean of median measured in full 4 minutes)?
p <- ggplot(df, aes(average_latency_to_enter_correct_side, mean_of_median_performance_on_each_ratio_full_four_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=30, y=0.5, label= "p = 0.0556, R-squared: 0.1098
        ", size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="mean_of_median_performance_on_each_ratio_
       full_four_minutes_data") +
  ggtitle ("Note:Does average latency to enter correct side predict 
           mean of median performance on each ratio (mean of median measured in full 4 minutes)?") +
  geom_smooth(method = "lm")

mod<- lm(df$mean_of_median_performance_on_each_ratio_full_four_minutes_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)
```

```{r}
#Does average latency to enter correct side predict mean of median performance on each ratio (mean of median measured in T30 to T50)?
p <- ggplot(df, aes(average_latency_to_enter_correct_side, mean_of_median_performance_on_each_ratio_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= "p = 0.04215, R-squared: 0.1306
        ", size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="mean_of_median_performance_on_each_ratio_T30_to_T50_data") +
  ggtitle ("Note:Does average latency to enter correct side predict
           mean of median performance on each ratio (mean of median measured in T30 to T50)?") +
  geom_smooth(method = "lm")

mod<- lm(df$mean_of_median_performance_on_each_ratio_T30_to_T50_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)
```


```{r}
#Does Mean of median performance on each ratio (full 4 minutes) predict average performance (full 4 minutes data)?
p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_full_four_minutes_data, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = 2.695e-16, R-squared: 0.8801
        ", size = 6, color = "black") + 
  labs(x= "mean_of_median_performance_on_each_ratio
_full_four_minutes_data",y="average_performance_across_all_9_testing_trials
       _using_full_4_minutes_data") +
  ggtitle ("Note:Does Mean of median performance on each ratio 
           (full 4 minutes) predict average performance (full 4 minutes data)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$mean_of_median_performance_on_each_ratio_full_four_minutes_data, na.rm = TRUE)
summary(mod)
```

```{r}
#Does Mean of median performance on each ratio (T30 to T50 data) predict average performance (T30 to T50 data)?
p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_T30_to_T50_data, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.6, label= "p = 8.579e-15, R-squared: 0.8693
        ", size = 6, color = "black") + 
  labs(x= "mean_of_median_performance_on_each_ratio_T30_to_T50_data",y="average_performance_across_all_9_testing_trials
       _using_T30_to_T50_data") +
  ggtitle ("Note:Does Mean of median performance on each ratio 
           (T30 to T50 data) predict average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$mean_of_median_performance_on_each_ratio_T30_to_T50_data, na.rm = TRUE)
summary(mod)

```



```{r}

#Does number of medians above 60% (full 4 minutes) predict latency to enter correct side?
df$number_of_medians_above_60_using_full_4_minutes_data <-as.character(df$number_of_medians_above_60_using_full_4_minutes_data)
p <- ggplot(df, aes(x=number_of_medians_above_60_using_full_4_minutes_data, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()
p

```

```{r}

#Does number of medians above 60% (T30 to T50) predict latency to enter correct side?
df$number_of_medians_above_60_using_T30_to_T50_data <-as.character(df$number_of_medians_above_60_using_T30_to_T50_data)
p <- ggplot(df, aes(x=number_of_medians_above_60_using_T30_to_T50_data, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()
p

```

```{r}

#Does number of medians above 60% (full four minutes) predict proportion of correct first choices?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_full_4_minutes_data, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()
p+  ggtitle ("Note:Does number of medians above 60% (full four minutes) 
             predict proportion of correct first choices?")

```


```{r}

#Does number of medians above 60% (T30 to T50) predict proportion of correct first choices?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_T30_to_T50_data, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does number of medians above 60% (T30 to T50)
              predict proportion of correct first choices?")

```


```{r}
#Does average number of entries predict average performance (full 4 minutes)?
p <- ggplot(df, aes(average_number_of_entries, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= "p = 0.08643, R-squared: 0.09798
        ", size = 6, color = "black") + 
  labs(x= "average_number_of_entries",y="average_performance_across_all_9_testing_trials
       _using_full_4_minutes_data") +
  ggtitle ("Note:Does average number of entries predict average performance (full 4 minutes)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_number_of_entries, na.rm = TRUE)
summary(mod)

```

```{r}
#Does average number of entries predict average performance (T30 to T50)?
p <- ggplot(df, aes(average_number_of_entries, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= "p = 0.02089, R-squared: 0.1707
        ", size = 6, color = "black") + 
  labs(x= "average_number_of_entries",y="average_performance_across_all_9_testing_trials
       _using_T30_to_T50_data") +
  ggtitle ("Note:Does average number of entries predict average performance (T30 to T50)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_number_of_entries, na.rm = TRUE)
summary(mod)

```


```{r}
#Does average number of entries predict proportion of correct choices?
p <- ggplot(df, aes(average_number_of_entries, proportion_of_correct_first_choices))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= "p = 0.5512, R-squared: 0.01238
        ", size = 6, color = "black") + 
  labs(x= "average_number_of_entries",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does average number of entries predict proportion of correct choices?") +
  geom_smooth(method = "lm")

mod<- lm(df$proportion_of_correct_first_choices ~ df$average_number_of_entries, na.rm = TRUE)
summary(mod)

```


```{r}
#Does average reaction time predict average performance (full 4 minutes)?
p <- ggplot(df, aes(average_reaction_time, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=20, y=0.1, label= "p = 0.1233, R-squared: 0.07992
        ", size = 6, color = "black") + 
  labs(x= "average_reaction_time",y="average_performance_across_all_9_testing_trials
       _using_full_4_minutes_data") +
  ggtitle ("Note:Does average reaction time predict 
           average performance (full 4 minutes)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

```


```{r}
#Does average reaction time predict average performance (T30 to T50)?
p <- ggplot(df, aes(average_reaction_time, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.5, label= "p = 0.04334, R-squared: 0.1334
        ", size = 6, color = "black") + 
  labs(x= "average_reaction_time",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Note:Does average reaction time predict average performance (T30 to T50)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

```

```{r}
#Does average reaction time predict proportion of correct choices?
p <- ggplot(df, aes(average_reaction_time, proportion_of_correct_first_choices))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.2, label= "p = 0.08333, R-squared: 0.09985
        ", size = 6, color = "black") + 
  labs(x= "average_reaction_time",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does average reaction time predict proportion of correct choices?") +
  geom_smooth(method = "lm")

mod<- lm(df$proportion_of_correct_first_choices ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

```

```{r}

#Does sex predict average performance over the full 4 minutes?
p <- ggplot(df, aes(x=sex, y=average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does sex predict average performance over the full 4 minutes?")

```


```{r}

#Does sex predict average performance over T30 to T50?
p <- ggplot(df, aes(x=sex, y=average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does sex predict average performance over T30 to T50?")

```


```{r}

#Does sex predict average latency to enter correct zone?
p <- ggplot(df, aes(x=sex, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does sex predict average latency to enter correct zone?")

```


```{r}

#Does sex predict proportion of correct choices?
p <- ggplot(df, aes(x=sex, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does sex predict proportion of correct choices?")

```


```{r}

#Does sex predict average number of entries?
p <- ggplot(df, aes(x=sex, y=average_number_of_entries)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does sex predict average number of entries?")

```


```{r}

#Does sex predict average reaction time?
p <- ggplot(df, aes(x=sex, y=average_reaction_time)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does sex predict average reaction time?")

```



```{r}
#Does size/age predict average perofmrance (full 4 minutes)?
p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= "p = 0.1531, R-squared: 0.06086
        ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Note:Does size/age predict average performance (full 4 minutes)? SEXES COMBINED") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$standard_length, na.rm = TRUE)
summary(mod)
```
```{r}
#Does size/age predict average perofmrance (full 4 minutes)?
p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_full_4_minutes_data, color = sex))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  #annotate("text", x=1600, y=0.2, label= "p = 0.1531, R-squared: 0.06086
  #      ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Note:Does size/age predict average performance (full 4 minutes)?") +
  geom_smooth(method = "lm")

```


```{r}
#Does size/age predict average performance(T30 to T50)?
p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1700, y=0.3, label= "p = 0.6725, R-squared: 0.005484
        ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Note:Does size/age predict average performance(T30 to T50)?SEXES COMBINED") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$standard_length, na.rm = TRUE)
summary(mod)
```




```{r}
#Does size/age predict average performance(T30 to T50)?
p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_T30_to_T50_data, color = sex))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  #annotate("text", x=1700, y=0.3, label= "p = 0.6725, R-squared: 0.005484
   #     ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Note:Does size/age predict average performance(T30 to T50)?") +
  geom_smooth(method = "lm")

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$standard_length, na.rm = TRUE)
summary(mod)
```



```{r}
#Does size/age predict proportion of correct choices?
p <- ggplot(df, aes(standard_length, proportion_of_correct_first_choices))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1700, y=0.1, label= "p = 0.3021, R-squared: 0.03223
        ", size = 6, color = "black") + 
  labs(x= "standard_length",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does size/age predict proportion of correct choices?SEXES COMBINED") +
  geom_smooth(method = "lm")

mod<- lm(df$proportion_of_correct_first_choices ~ df$standard_length, na.rm = TRUE)
summary(mod)

```

```{r}
#Does size/age predict proportion of correct choices?
p <- ggplot(df, aes(standard_length, proportion_of_correct_first_choices, color = sex))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
 # annotate("text", x=1700, y=0.1, label= "p = 0.3021, R-squared: 0.03223
  #      ", size = 6, color = "black") + 
  labs(x= "standard_length",y="proportion_of_correct_first_choices") +
  ggtitle ("Note:Does size/age predict proportion of correct choices?") +
  geom_smooth(method = "lm")


```



```{r}
#Does size/age predict average latency to enter correct side?
p <- ggplot(df, aes(standard_length, average_latency_to_enter_correct_side))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1800, y=75, label= "p = 0.03616, R-squared: 0.1263
        ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_latency_to_enter_correct_side") +
  ggtitle ("Note:Does size/age predict average latency to enter correct side? SEXES COMBINED") +
  geom_smooth(method = "lm")

mod<- lm(df$average_latency_to_enter_correct_side ~ df$standard_length, na.rm = TRUE)
summary(mod)

```


```{r}
#Does size/age predict average latency to enter correct side?
p <- ggplot(df, aes(standard_length, average_latency_to_enter_correct_side, color = sex))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  #annotate("text", x=1800, y=75, label= "p = 0.03616, R-squared: 0.1263
  #      ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_latency_to_enter_correct_side") +
  ggtitle ("Note:Does size/age predict average latency to enter correct side?") +
  geom_smooth(method = "lm")


```


```{r}
#Does size/age predict average number of entries?
p <- ggplot(df, aes(standard_length, average_number_of_entries))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", 1800, y=100, label= "p = 0.001527, R-squared: 0.2885
        ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_number_of_entries") +
  ggtitle ("Note:Does size/age predict average number of entries?SEXES COMBINED") +
  geom_smooth(method = "lm")

mod<- lm(df$average_number_of_entries ~ df$standard_length, na.rm = TRUE)
summary(mod)
```

```{r}
#Does size/age predict average number of entries?
p <- ggplot(df, aes(standard_length, average_number_of_entries, color = sex))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  #annotate("text", 1800, y=100, label= "p = 0.001527, R-squared: 0.2885
  #      ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_number_of_entries") +
  ggtitle ("Note:Does size/age predict average number of entries?") +
  geom_smooth(method = "lm")


```



```{r}
#Does size/age predict reaction time?
p <- ggplot(df, aes(standard_length, average_reaction_time))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1800, y=30, label= "p = 0.02407, R-squared: 0.1584
        ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_reaction_time") +
  ggtitle ("Note:Does size/age predict reaction time? SEXES COMBINED") +
  geom_smooth(method = "lm")

mod<- lm(df$average_reaction_time ~ df$standard_length, na.rm = TRUE)
summary(mod)

```

```{r}
#Does size/age predict reaction time?
p <- ggplot(df, aes(standard_length, average_reaction_time, color = sex))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  #annotate("text", x=1800, y=30, label= "p = 0.02407, R-squared: 0.1584
  #      ", size = 6, color = "black") + 
  labs(x= "standard_length",y="average_reaction_time") +
  ggtitle ("Note:Does size/age predict reaction time?") +
  geom_smooth(method = "lm")


```








```{r}

#Does order predict average performance over the full 4 minutes?
p <- ggplot(df, aes(x=order, y=average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does order predict average performance over the full 4 minutes?")

```


```{r}

#Does order predict performance over T30 to T50?
p <- ggplot(df, aes(x=order, y=average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does order predict performance over T30 to T50?")

```


```{r}

#Does order predict average latency to enter correct side?
p <- ggplot(df, aes(x=order, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does order predict average latency to enter correct side?")

```


```{r}

#Does order predict proportion of correct choices?
p <- ggplot(df, aes(x=order, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does order predict proportion of correct choices?")

```


```{r}

#Does order predict average number of entries?
p <- ggplot(df, aes(x=order, y=average_number_of_entries)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does order predict average number of entries?")

```



```{r}

#Does order predict average reaction time?
p <- ggplot(df, aes(x=order, y=average_reaction_time)) + 
  geom_boxplot()
p +  ggtitle ("Note:Does order predict average reaction time?")

```




```{r}

p <- ggplot(df, aes(XXX, XXX))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= "p = x0.007277, R-squared:  x0.1987
        ", size = 6, color = "black") + 
  labs(x= "XXX",y="XXX") +
  ggtitle ("Note:XXX") +
  geom_smooth(method = "lm")

mod<- lm(df$XXX ~ df$XXX, na.rm = TRUE)
summary(mod)
```



4. See how consistent individuals are across trials within the same individuals (so will have an average repeatibility score?)
Performance over the full 4 minutes
Performance over T30 to T50
Which side was chosen first


NOTE: Here's the column names coming from df.sum:

"fish_name"                                                                                                        
  [2] "sex"                                                                                                              
  [3] "standard_length"                                                                                                  
  [4] "order"   
  
------------------------------------------------------------------------
  
[149] "average_number_of_entries"                                                                                        
[150] "average_reaction_time"                                                                                            
[151] "average_performance_across_all_9_testing_trials_using_full_4_minutes_data"                                        
[152] "average_performance_across_all_9_testing_trials_using_T30_to_T50_data"                                            
[153] "total_number_of_testing_trials_using_full_4_minutes_data"                                                         
[154] "total_number_of_testing_trials_using_T30_to_T50_data"                                                             
[155] "number_of_trials_on_0.50_ratio_using_full_4_minutes_data"                                                         
[156] "number_of_trials_on_0.67_ratio_using_full_4_minutes_data"                                                         
[157] "number_of_trials_on_0.75_ratio_using_full_4_minutes_data"                                                         
[158] "number_of_trials_on_0.50_ratio_using_T30_to_T50_data"                                                             
[159] "number_of_trials_on_0.67_ratio_using_T30_to_T50_data"                                                             
[160] "number_of_trials_on_0.75_ratio_using_T30_to_T50_data"                                                             
[161] "median_performance_on_0.50_ratio_using_full_4_minutes_data"                                                       
[162] "median_performance_on_0.67_ratio_using_full_4_minutes_data"                                                       
[163] "median_performance_on_0.75_ratio_using_full_4_minutes_data"                                                       
[164] "median_performance_on_0.50_ratio_using_T30_to_T50_data"                                                           
[165] "median_performance_on_0.67_ratio_using_T30_to_T50_data"                                                           
[166] "median_performance_on_0.75_ratio_using_T30_to_T50_data"                                                           
[167] "number_of_medians_above_60_using_full_4_minutes_data"                                                             
[168] "number_of_medians_above_60_using_T30_to_T50_data"                                                                 
[169] "shapiro_wilk_test_p_value_using_full_4_minutes_data"                                                              
[170] "was_average_performance_significantly_different_from_0.5_full_4_minutes_p_value_of_either_t_test_or_wilcox"       
[171] "shapiro_wilk_test_p_value_using_T30_to_T50_data"                                                                  
[172] "was_average_performance_significantly_different_from_0.5_T30_to_T50_p_value_of_either_t_test_or_wilcox"           
[173] "learning_category_according_to_etheredge_T30_to_T50"                                                              
[174] "learning_category_according_to_etheredge_full_4_minutes"                                                          
[175] "average_latency_to_enter_correct_side"                                                                            
[176] "average_latency_to_enter_incorrect_side"                                                                          
[177] "proportion_of_correct_first_choices"                                                                              
[178] "number_of_trials_in_a_row_greater_than_60_percent_full_4_minutes"                                                 
[179] "number_of_trials_in_a_row_greater_than_60_percent_T30_to_T50"                                                     
[180] "number_of_trials_in_a_row_correct_choice_first"                                                                   
[181] "mean_of_median_performance_on_each_ratio_full_four_minutes_data"                                                  
[182] "mean_of_median_performance_on_each_ratio_T30_to_T50_data" 

------------------------------------------------------------------------

 [5] "Trial_9_1_correctside"                                                                                            
  [6] "Trial_9_1_ratio"                                                                                                  
  [7] "Trial_9_1_total_entries"                                                                                          
  [8] "Trial_9_1_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens" 
  [9] "Trial_9_1_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"     
 [10] "Trial_9_1_was_performance_over_full_4_minutes_greater_than_60_percent"                                            
 [11] "Trial_9_1_was_performance_T30_to_T50_greater_than_60_percent"                                                     
 [12] "Trial_9_1_reaction_time"                                                                                          
 [13] "Trial_9_1_latency_to_enter_correct_side"                                                                          
 [14] "Trial_9_1_latency_to_enter_incorrect_side"                                                                        
 [15] "Trial_9_1_screen_entered_first"                                                                                   
 [16] "Trial_9_1_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                           
 [17] "Trial_9_1_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                         
 [18] "Trial_9_1_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                               
 [19] "Trial_9_1_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                             
 [20] "Trial_9_3_correctside"                                                                                            
 [21] "Trial_9_3_ratio"                                                                                                  
 [22] "Trial_9_3_total_entries"                                                                                          
 [23] "Trial_9_3_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens" 
 [24] "Trial_9_3_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"     
 [25] "Trial_9_3_was_performance_over_full_4_minutes_greater_than_60_percent"                                            
 [26] "Trial_9_3_was_performance_T30_to_T50_greater_than_60_percent"                                                     
 [27] "Trial_9_3_reaction_time"                                                                                          
 [28] "Trial_9_3_latency_to_enter_correct_side"                                                                          
 [29] "Trial_9_3_latency_to_enter_incorrect_side"                                                                        
 [30] "Trial_9_3_screen_entered_first"                                                                                   
 [31] "Trial_9_3_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                           
 [32] "Trial_9_3_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                         
 [33] "Trial_9_3_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                               
 [34] "Trial_9_3_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                             
 [35] "Trial_9_5_correctside"                                                                                            
 [36] "Trial_9_5_ratio"                                                                                                  
 [37] "Trial_9_5_total_entries"                                                                                          
 [38] "Trial_9_5_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens" 
 [39] "Trial_9_5_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"     
 [40] "Trial_9_5_was_performance_over_full_4_minutes_greater_than_60_percent"                                            
 [41] "Trial_9_5_was_performance_T30_to_T50_greater_than_60_percent"                                                     
 [42] "Trial_9_5_reaction_time"                                                                                          
 [43] "Trial_9_5_latency_to_enter_correct_side"                                                                          
 [44] "Trial_9_5_latency_to_enter_incorrect_side"                                                                        
 [45] "Trial_9_5_screen_entered_first"                                                                                   
 [46] "Trial_9_5_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                           
 [47] "Trial_9_5_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                         
 [48] "Trial_9_5_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                               
 [49] "Trial_9_5_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                             
 [50] "Trial_10_1_correctside"                                                                                           
 [51] "Trial_10_1_ratio"                                                                                                 
 [52] "Trial_10_1_total_entries"                                                                                         
 [53] "Trial_10_1_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [54] "Trial_10_1_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
 [55] "Trial_10_1_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
 [56] "Trial_10_1_was_performance_T30_to_T50_greater_than_60_percent"                                                    
 [57] "Trial_10_1_reaction_time"                                                                                         
 [58] "Trial_10_1_latency_to_enter_correct_side"                                                                         
 [59] "Trial_10_1_latency_to_enter_incorrect_side"                                                                       
 [60] "Trial_10_1_screen_entered_first"                                                                                  
 [61] "Trial_10_1_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
 [62] "Trial_10_1_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
 [63] "Trial_10_1_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
 [64] "Trial_10_1_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
 [65] "Trial_10_3_correctside"                                                                                           
 [66] "Trial_10_3_ratio"                                                                                                 
 [67] "Trial_10_3_total_entries"                                                                                         
 [68] "Trial_10_3_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [69] "Trial_10_3_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
 [70] "Trial_10_3_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
 [71] "Trial_10_3_was_performance_T30_to_T50_greater_than_60_percent"                                                    
 [72] "Trial_10_3_reaction_time"                                                                                         
 [73] "Trial_10_3_latency_to_enter_correct_side"                                                                         
 [74] "Trial_10_3_latency_to_enter_incorrect_side"                                                                       
 [75] "Trial_10_3_screen_entered_first"                                                                                  
 [76] "Trial_10_3_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
 [77] "Trial_10_3_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
 [78] "Trial_10_3_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
 [79] "Trial_10_3_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
 [80] "Trial_10_5_correctside"                                                                                           
 [81] "Trial_10_5_ratio"                                                                                                 
 [82] "Trial_10_5_total_entries"                                                                                         
 [83] "Trial_10_5_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [84] "Trial_10_5_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
 [85] "Trial_10_5_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
 [86] "Trial_10_5_was_performance_T30_to_T50_greater_than_60_percent"                                                    
 [87] "Trial_10_5_reaction_time"                                                                                         
 [88] "Trial_10_5_latency_to_enter_correct_side"                                                                         
 [89] "Trial_10_5_latency_to_enter_incorrect_side"                                                                       
 [90] "Trial_10_5_screen_entered_first"                                                                                  
 [91] "Trial_10_5_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
 [92] "Trial_10_5_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
 [93] "Trial_10_5_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
 [94] "Trial_10_5_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
 [95] "Trial_11_1_correctside"                                                                                           
 [96] "Trial_11_1_ratio"                                                                                                 
 [97] "Trial_11_1_total_entries"                                                                                         
 [98] "Trial_11_1_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [99] "Trial_11_1_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
[100] "Trial_11_1_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
[101] "Trial_11_1_was_performance_T30_to_T50_greater_than_60_percent"                                                    
[102] "Trial_11_1_reaction_time"                                                                                         
[103] "Trial_11_1_latency_to_enter_correct_side"                                                                         
[104] "Trial_11_1_latency_to_enter_incorrect_side"                                                                       
[105] "Trial_11_1_screen_entered_first"                                                                                  
[106] "Trial_11_1_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
[107] "Trial_11_1_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
[108] "Trial_11_1_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
[109] "Trial_11_1_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
[110] "Trial_11_3_correctside"                                                                                           
[111] "Trial_11_3_ratio"                                                                                                 
[112] "Trial_11_3_total_entries"                                                                                         
[113] "Trial_11_3_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
[114] "Trial_11_3_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
[115] "Trial_11_3_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
[116] "Trial_11_3_was_performance_T30_to_T50_greater_than_60_percent"                                                    
[117] "Trial_11_3_reaction_time"                                                                                         
[118] "Trial_11_3_latency_to_enter_correct_side"                                                                         
[119] "Trial_11_3_latency_to_enter_incorrect_side"                                                                       
[120] "Trial_11_3_screen_entered_first"                                                                                  
[121] "Trial_11_3_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
[122] "Trial_11_3_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
[123] "Trial_11_3_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
[124] "Trial_11_3_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
[125] "Trial_11_5_correctside"                                                                                           
[126] "Trial_11_5_ratio"                                                                                                 
[127] "Trial_11_5_total_entries"                                                                                         
[128] "Trial_11_5_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
[129] "Trial_11_5_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
[130] "Trial_11_5_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
[131] "Trial_11_5_was_performance_T30_to_T50_greater_than_60_percent"                                                    
[132] "Trial_11_5_reaction_time"                                                                                         
[133] "Trial_11_5_latency_to_enter_correct_side"                                                                         
[134] "Trial_11_5_latency_to_enter_incorrect_side"                                                                       
[135] "Trial_11_5_screen_entered_first"                                                                                  
[136] "Trial_11_5_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
[137] "Trial_11_5_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
[138] "Trial_11_5_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
[139] "Trial_11_5_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
[140] "Trial_9_1_was_fish_in_correct_screen_at_start"                                                                    
[141] "Trial_9_3_was_fish_in_correct_screen_at_start"                                                                    
[142] "Trial_9_5_was_fish_in_correct_screen_at_start"                                                                    
[143] "Trial_10_1_was_fish_in_correct_screen_at_start"                                                                   
[144] "Trial_10_3_was_fish_in_correct_screen_at_start"                                                                   
[145] "Trial_10_5_was_fish_in_correct_screen_at_start"                                                                   
[146] "Trial_11_1_was_fish_in_correct_screen_at_start"                                                                   
[147] "Trial_11_3_was_fish_in_correct_screen_at_start"                                                                   
[148] "Trial_11_5_was_fish_in_correct_screen_at_start"                             

```{r}

```





