---
title: "Comparative Cognition Numerosity Analysisof Cowlog Data Part V"
author: "Kelly Wallace"
date: "April 12, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is the last script! This makes the actual full data frame with numerosity, shuttlebox, and detour information combined. For now I've got the shuttlebox data analysis in here. 

Note for later on- the boxplots with sex I was having trouble putting hte labels on so I hardcoded them into the title, need to fix it. 

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(rmarkdown)
library(knitr)
library(readr)
library(utils)
library(EnvStats)

shuttle<-read.csv("C:/Users/Kelly/Desktop/Grad School/Cummings Lab/Comparative Cognition/Shuttlebox/shuttlebox_data_april_25_2018.csv")

det<-read.csv("C:/Users/Kelly/Desktop/Grad School/Cummings Lab/Comparative Cognition/Detour/detour_data_for_R_April_5_2018.csv")

num<-read.csv("C:/Users/Kelly/Desktop/Grad School/Cummings Lab/Comparative Cognition/Comparative Cognition R Scripts/Numerosity Comparative Cognition Full Dataset May_7_2018.csv")

df.full<- left_join(det,shuttle, by = 'fish_name')
df.full<- left_join(df.full,num, by = 'fish_name') #need to not join shuttlebox twice!
df.full$detour_trial_1_did_fish_solve_barrier_problem <-as.character(df.full$detour_trial_1_did_fish_solve_barrier_problem)


#WRITE IT OUT IF NEEDED
write_csv(df.full, 'Full_Comparative_Cognition_Data_Detour_Shuttlebox_Numerosity_May_1_2018.csv')

```

Shuttlebox Measures:

average distance from correct stimulus during gaps
average distance from correct stimulus during stim
shuttlebox slope
binned average distance from correct stimulus during stim
binned average distance from correct stimulus during gaps
binned shuttlebox slope

shuttlebox_average_proportion_of_time_on_correct_side_during_stimulus
shuttlebox_average_proportion_of_time_on_correct_side_during_gaps
shuttlebox_proportion_of_time_on_correct_side_during_stimulus_slope_across_presentations
shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations
binned shuttlebox_average_proportion_of_time_on_correct_side_during_stimulus
binned  shuttlebox_average_proportion_of_time_on_correct_side_during_gaps
binned shuttlebox_proportion_of_time_on_correct_side_during_stimulus_slope_across_presentations
binned shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations
AND THE 23 presentation filtered versions of those listed above




```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have lower average distances from the correct side in shuttlebox?

test<-t.test(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=shuttlebox_average_distance_from_correct_stimulus_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem have 
          lower average distances from the correct side in shuttlebox?') +
  geom_text(x=1, y=590, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```

```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict average distance from the correct side in shuttlebox?

mod<- lm(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem predict 
           average distance from the correct side in shuttlebox?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) predict average distance from the correct side in shuttlebox?
mod<- lm(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) predict
           average distance from the correct side in shuttlebox?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict average distance from the correct side in shuttlebox?
mod<- lm(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity latency to enter the correct side 
           predict average distance from the correct side in shuttlebox?") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict average distance from the correct side in shuttlebox? latency filtered only correct
mod<- lm(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity latency to enter the correct side (filtered correct only)
           predict average distance from the correct side in shuttlebox?") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average distance from the correct side?
test<-t.test(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=shuttlebox_average_distance_from_correct_stimulus_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox average 
          distance from the correct side? p (wilcox)= 0.189') #+
  #geom_text(label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          #p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```

```{r, echo=FALSE, message=FALSE}
#Does numerosity average number of entries predict average distance from the correct side in shuttlebox?
mod<- lm(df.full$shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict average distance from the correct side in shuttlebox?") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have more negative shuttlebox slope of learning?
test<-t.test(df.full$shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem have 
          more negative shuttlebox slope of learning?') +
  geom_text(x=1, y=5, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of learning?
mod<- lm(df.full$shuttlebox_slope ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of learning?") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) shuttlebox slope of learning?
mod<- lm(df.full$shuttlebox_slope ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) shuttlebox slope of learning?") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of learning?
mod<- lm(df.full$shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of learning?") +
  geom_smooth(method = "lm")

```
```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of learning?
mod<- lm(df.full$shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of learning?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox slope of learning?
test<-t.test(df.full$shuttlebox_slope~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_slope~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of learning?') +
  geom_text(x=1, y=3, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of learning?

mod<- lm(df.full$shuttlebox_slope ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0.8,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict ahuttlebox slope of learning?") +
  geom_smooth(method = "lm")

```








```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have more negative shuttlebox slope of learning?BINNED
test<-t.test(df.full$binned_shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$binned_shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=binned_shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem have 
          more negative shuttlebox slopes of learning?BINNED') +
  geom_text(x=1, y=5, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of learning?BINNED
mod<- lm(df.full$binned_shuttlebox_slope ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of learning?BINNED") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) shuttlebox slope of learning?BINNED
mod<- lm(df.full$binned_shuttlebox_slope ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) shuttlebox slope of learning?BINNED") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of learning?BINNED
mod<- lm(df.full$binned_shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of learning?BINNED") +
  geom_smooth(method = "lm")

```
```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of learning?BINNED
mod<- lm(df.full$binned_shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of learning?BINNED") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox slope of learning?BINNED
test<-t.test(df.full$binned_shuttlebox_slope~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$binned_shuttlebox_slope~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=binned_shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of learning?BINNED') +
  geom_text(x=1, y=3, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of learning?BINNED

mod<- lm(df.full$binned_shuttlebox_slope ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0.8,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict shuttlebox slope of learning?BINNED") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have more negative shuttlebox average proportion of time on the correct side during gaps?
test<-t.test(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem predict shuttlebox average proportion
          of time on the correct side during gaps?') +
  geom_text(x=1, y=0.4, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox average proportion of time on the correct side during gaps?
mod<- lm(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox average proportion 
           of time on the correct side during gaps?") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) shuttlebox average proportion of time on the correct side during gaps?
mod<- lm(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) shuttlebox average 
           proportion of time on the correct side during gaps?") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox average proportion of time on the correct side during gaps?
mod<- lm(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox average proportion of 
           time on the correct side during gaps?") +
  geom_smooth(method = "lm")

```
```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox average proportion of time on the correct side during gaps?
mod<- lm(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox average proportion 
           of time on the correct side during gaps?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average proportion of time on the correct side during gaps?
test<-t.test(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox average proportion of time on the correct side during gaps?') +
  geom_text(x=1, y=0.45, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox average proportion of time on the correct side during gaps?

mod<- lm(df.full$shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict average proportion of time on 
           the correct side during gaps") +
  geom_smooth(method = "lm")

```











```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem  predict shuttlebox slope of the proportion correct side across gaps?
test<-t.test(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem predict 
          shuttlebox slope of the proportion correct side across gaps') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of the proportion correct side across gaps?
mod<- lm(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of the proportion correct side across gaps") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) predict shuttlebox slope of the proportion correct side across gaps?
mod<- lm(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) predict shuttlebox 
           slope of the proportion correct side across gaps") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of the proportion correct side across gaps?
mod<- lm(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of the proportion correct side across gaps") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of the proportion correct side across gaps?
mod<- lm(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of the proportion correct side across gaps") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average predict shuttlebox slope of the proportion correct side across gaps?
test<-t.test(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of the proportion correct side across gapss?') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of the proportion correct side across gaps?

mod<- lm(df.full$shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict predict shuttlebox slope of the proportion correct side across gaps") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem  predict shuttlebox slope of the proportion correct side across gaps?BINNED
test<-t.test(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem predict 
          shuttlebox slope of the proportion correct side across gaps BINNED') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of the proportion correct side across gaps?BINNED
mod<- lm(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of the proportion correct side across gaps BINNED") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) predict shuttlebox slope of the proportion correct side across gaps?BINNED
mod<- lm(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) predict shuttlebox 
           slope of the proportion correct side across gaps BINNED") +
  geom_smooth(method = "lm")

```




```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of the proportion correct side across gaps?BINNED
mod<- lm(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of the proportion correct side across gaps BINNED") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of the proportion correct side across gaps?BINNED
mod<- lm(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of the proportion correct side across gaps BINNED") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average predict shuttlebox slope of the proportion correct side across gaps? BINNED
test<-t.test(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of the proportion correct side across gaps?BINNED') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of the proportion correct side across gaps?BINNED

mod<- lm(df.full$binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict predict shuttlebox slope of the proportion 
           correct side across gaps BINNED") +
  geom_smooth(method = "lm")

```


#############
#############
#############
#############
#############

OK from here on out everything is going to be repeated but the shuttlebox data was cut off after 23 presentations, which was on average when fish stopped participating and "camped out" on one side for the rest of the trial




```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have lower average distances from the correct side in shuttlebox? stops at 23

test<-t.test(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem have 
          lower average distances from the correct side in shuttlebox? stops at 23') +
  geom_text(x=1, y=590, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```

```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict average distance from the correct side in shuttlebox? stops at 23

mod<- lm(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem predict 
           average distance from the correct side in shuttlebox? stops at 23") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) predict average distance from the correct side in shuttlebox? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) predict
           average distance from the correct side in shuttlebox? stops at 23") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict average distance from the correct side in shuttlebox? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity latency to enter the correct side 
           predict average distance from the correct side in shuttlebox? stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict average distance from the correct side in shuttlebox? latency filtered only correct stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity latency to enter the correct side (filtered correct only)
           predict average distance from the correct side in shuttlebox? stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average distance from the correct side? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox average 
          distance from the correct side? p (wilcox)= 0.189  
          stops at 23') #+
  #geom_text(label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          #p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```

```{r, echo=FALSE, message=FALSE}
#Does numerosity average number of entries predict average distance from the correct side in shuttlebox? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, twentythree_filtered_shuttlebox_average_distance_from_correct_stimulus_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=600,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict average distance from the correct side in shuttlebox? stops at 23") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have more negative shuttlebox slope of learning? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=twentythree_filtered_shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem have 
          more negative shuttlebox slope of learning? stops at 23') +
  geom_text(x=1, y=5, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of learning? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_slope ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(twentythree_filtered_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, twentythree_filtered_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of learning? stops at 23") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) shuttlebox slope of learning? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_slope ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(twentythree_filtered_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, twentythree_filtered_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) shuttlebox slope of learning? stops at 23") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of learning? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(twentythree_filtered_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, twentythree_filtered_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of learning? stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of learning? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(twentythree_filtered_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, twentythree_filtered_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of learning? stops at 23") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox slope of learning? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_slope~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_slope~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=twentythree_filtered_shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of learning? stops at 23') +
  geom_text(x=1, y=3, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of learning? stops at 23

mod<- lm(df.full$twentythree_filtered_shuttlebox_slope ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(twentythree_filtered_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, twentythree_filtered_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0.8,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict ahuttlebox slope of learning? stops at 23") +
  geom_smooth(method = "lm")

```








```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have more negative shuttlebox slope of learning?BINNED stops at 23
test<-t.test(df.full$twentythree_filtered_binned_shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_binned_shuttlebox_slope~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=twentythree_filtered_binned_shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem have 
          more negative shuttlebox slopes of learning?BINNED stops at 23') +
  geom_text(x=1, y=5, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of learning?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_slope ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, twentythree_filtered_binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of learning?BINNED stops at 23") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) shuttlebox slope of learning?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_slope ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, twentythree_filtered_binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) shuttlebox slope of learning?BINNED stops at 23") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of learning?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, twentythree_filtered_binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of learning?BINNED stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of learning?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_slope ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, twentythree_filtered_binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.3,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of learning?BINNED stops at 23") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox slope of learning?BINNED stops at 23
test<-t.test(df.full$twentythree_filtered_binned_shuttlebox_slope~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_binned_shuttlebox_slope~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=twentythree_filtered_binned_shuttlebox_slope)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of learning?BINNED stops at 23') +
  geom_text(x=1, y=3, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of learning?BINNED stops at 23

mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_slope ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_slope)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, twentythree_filtered_binned_shuttlebox_slope))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0.8,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict shuttlebox slope of learning?BINNED stops at 23") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem have more negative shuttlebox average proportion of time on the correct side during gaps? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem predict shuttlebox average proportion
          of time on the correct side during gaps? stops at 23') +
  geom_text(x=1, y=0.4, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox average proportion of time on the correct side during gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox average proportion 
           of time on the correct side during gaps? stops at 23") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) shuttlebox average proportion of time on the correct side during gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) shuttlebox average 
           proportion of time on the correct side during gaps? stops at 23") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox average proportion of time on the correct side during gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox average proportion of 
           time on the correct side during gaps? stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox average proportion of time on the correct side during gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox average proportion 
           of time on the correct side during gaps? stops at 23") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average proportion of time on the correct side during gaps? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox average proportion of time on the correct side during gaps?
           stops at 23') +
  geom_text(x=1, y=0.45, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox average proportion of time on the correct side during gaps? stops at 23

mod<- lm(df.full$twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, twentythree_filtered_shuttlebox_average_proportion_of_time_on_correct_side_during_gaps))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0.45,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict average proportion of time on 
           the correct side during gaps stops at 23") +
  geom_smooth(method = "lm")

```











```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem  predict shuttlebox slope of the proportion correct side across gaps? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem predict 
          shuttlebox slope of the proportion correct side across gaps stops at 23') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of the proportion correct side across gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of the proportion correct side across gaps stops at 23") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) predict shuttlebox slope of the proportion correct side across gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) predict shuttlebox 
           slope of the proportion correct side across gaps stops at 23") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of the proportion correct side across gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of the proportion correct side across gaps  stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of the proportion correct side across gaps? stops at 23
mod<- lm(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of the proportion correct side across gaps stops at 23") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average predict shuttlebox slope of the proportion correct side across gaps? stops at 23
test<-t.test(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of the proportion correct side across gaps stops at 23?') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of the proportion correct side across gaps? stops at 23

mod<- lm(df.full$twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, twentythree_filtered_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict predict shuttlebox slope of the proportion correct side across gaps stops at 23") +
  geom_smooth(method = "lm")

```






```{r, echo=FALSE, message=FALSE}
#Do fish that solve the detour barrier problem  predict shuttlebox slope of the proportion correct side across gaps?BINNED stops at 23
test<-t.test(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$detour_trial_1_did_fish_solve_barrier_problem)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=detour_trial_1_did_fish_solve_barrier_problem, y=twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Do fish that solve the detour barrier problem predict 
          shuttlebox slope of the proportion correct side across gaps 
          BINNED stops at 23') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```



```{r, echo=FALSE, message=FALSE}
#Does latency to solve the detour barrier problem predict shuttlebox slope of the proportion correct side across gaps?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)
summary(mod)

number <- df.full %>% filter(!is.na(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(detour_trial_1_barrier_problem_time_around_barrier_minus_time_to_contact_barrier, twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=150, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does latency to solve the detour barrier problem 
           predict shuttlebox slope of the proportion correct side across gaps 
           BINNED stops at 23") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE}
#Does numerosity average performance (T30 to T50) predict shuttlebox slope of the proportion correct side across gaps?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_performance_across_all_9_testing_trials_using_T30_to_T50_data)
summary(mod)

number <- df.full %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.5, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average performance (T30 to T50) predict shuttlebox 
           slope of the proportion correct side across gaps BINNED stops at 23") +
  geom_smooth(method = "lm")

```




```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side predict shuttlebox slope of the proportion correct side across gaps?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side, twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side 
           predict shuttlebox slope of the proportion correct side across gaps 
           BINNED stops at 23") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does numerosity latency to enter the correct side (filtered) predict shuttlebox slope of the proportion correct side across gaps?BINNED stops at 23
mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_latency_to_enter_correct_side_filtered_just_correct_choice)
summary(mod)

number <- df.full %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Note:Does numerosity latency to enter the correct side (filtered)
           predict shuttlebox slope of the proportion correct side across gaps
           BINNED stops at 23") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does sex predict shuttlebox average predict shuttlebox slope of the proportion correct side across gaps? BINNED stops at 23
test<-t.test(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations~df.full$sex.x)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df.full, aes(x=sex.x, y=twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('#Does sex predict shuttlebox slope of the proportion correct side across gaps?
          BINNED stops at 23') +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p


```


```{r, echo=FALSE, message=FALSE}
#Does average_number_entries predict shuttlebox slope of the proportion correct side across gaps?BINNED stops at 23

mod<- lm(df.full$twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations ~ df.full$average_number_of_entries)
summary(mod)

number <- df.full %>% filter(!is.na(average_number_of_entries)) %>% filter(!is.na(twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df.full, aes(average_number_of_entries, twentythree_filtered_binned_shuttlebox_proportion_of_time_on_correct_side_during_gaps_slope_across_presentations))
p + geom_point(size = 3) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=55, y=0,label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  ggtitle ("Does numerosity average number of entries 
           predict predict shuttlebox slope of the proportion 
           correct side across gaps BINNED 
           stops at 23") +
  geom_smooth(method = "lm")

```




