---
title: "Comparative Cognition Numerosity Analysis of Cowlog data Part II"
author: "Kelly Wallace"
date: "March 16, 2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=6)
```

This document takes the output from "Comparative Cognition Numerosity Cowlog Analysis.Rmd" and graphs relevant data. 
 Comparative Cognition Numerosity Cowlog Analysis.Rmd takes all the individual cowlog score sheets for numerosity and summarized them into one datasheet, df.sum

Individuals in the data output from the first rmd: 
wahida, wheatley,winnifred, wisteria,wayne, gabi,wile, wyatt,wedelia, gavin,gretchen, wade,willis, gloria,waldhurga, garrison,george, waverly,wilbur, wildflower,gemma, gertrude,grayson, watson,gary, winter,georgiafixed, wendy,gladys, gibson,gina, griffin,gabriel, winona,gideon,gordon, 

ORDER OF ANALYSIS:
1. Pairwise comparisons of the following (one value per individual) performance metrics:
Average performance over full 4 minutes
Average performance over T30 to T50
Proportion of correct first choices
Average latency to approach correct side
Mean of median perofomance on each ratio
number of medians above 0.60 using full 4 minutes data
number of medians above 0.60 using full 4 minutes data


2. Pairwise comparison of the performance metrics (one value per individual) to the following behavior metrics:
Average number of entries
Average reaction time

3. Investigating other factors (compare performance to):
sex, 
size, 
order,

4. See how consistent individuals are across trials within the same individuals (so will have an average repeatibility score?)
Performance over the full 4 minutes
Performance over T30 to T50
Which side was chosen first

STATS:
To determine if one slope is significantly different from zero:
mod<- lm(y ~ x)
summary(mod)

T-test to determine if two groups (boxplot with 2 groups) have significantly different distributions:
t.test(y~x) # where y is numeric and x is a binary factor 

Nonparametric version of a t test
wilcox.test(y,x)
(Note from previous script: you can use a shapiro test to test for normality)

one-way ANOVA to determine if any one group (boxplot with > 2 groups)has a significantly different distribution
fit <- aov(y ~ A, data=mydataframe) 
summary(fit)

Nonparametric version of a one-way ANOVA
kruskal.test(y ~ x, data = mydata)

Linerar model finding the interaction term:
mod<-lm(y~a+b)
e.g number of entries x performance (latency to enter correct) - does this relationship vary by sex?
mod<-lm(performance~entries+sex)
summary(mod)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(rmarkdown)
library(knitr)
library(readr)
library(utils)
library(EnvStats)
library(coin)


df<- read_csv("C:/Users/Kelly/Desktop/Grad School/Cummings Lab/Comparative Cognition/Comparative Cognition R Scripts/Numerosity Comparative Cognition Full Dataset May_7_2018.csv", col_names = TRUE, col_types = NULL)

df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)
df$did_fish_have_a_median_above_60<-as.factor(df$did_fish_have_a_median_above_60)
df$did_fish_have_at_least_two_medians_above_60<-as.factor(df$did_fish_have_at_least_two_medians_above_60)
df.males<-filter(df, df$sex == "M")
df.males$sex_code<-0

df.females<-filter(df, df$sex == "F")
df.females$sex_code<-1

df<-full_join(df.males,df.females)

View(df)



```

Template:


mod<- lm(df$XXX ~ df$XXX, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(XXX)) %>% filter(!is.na(XXX)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(XXX, XXX))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "XXX",y="XXX") +
  ggtitle ("XXX") +
  geom_smooth(method = "lm")


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average performance over just T30 to T50 predict average performance over the full 4 minutes?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_performance_across_all_9_testing_trials_using_T30_to_T50_data, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_performance_across_all_9_testing_trials_using_T30_to_T50_data",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Does average performance over just T30 to T50 predict 
           average performance over the full 4 minutes?") +
  geom_smooth(method = "lm", size = 2, fill = "light gray", color = "deepskyblue4")+
         theme(axis.text=element_text(size=12),
         axis.title=element_text(size=14))+
         theme(axis.line.y = element_line(color="gray", size = 1))+
         theme(axis.line.x = element_line(color="gray", size = 1))+ 
         theme(panel.background = element_blank())+ 
         theme(plot.title = element_text(size=14))


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$proportion_of_correct_first_choices, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

#Does proportion of correct first choices predict average performance (T30 to T50 data)?
p <- ggplot(df, aes(proportion_of_correct_first_choices, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.63, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "proportion_of_correct_first_choices",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does proportion of correct first 
           choices predict average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")



```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does proportion of correct first choices predict average performance (full four minutes data)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$proportion_of_correct_first_choices, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(proportion_of_correct_first_choices, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "proportion_of_correct_first_choices",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Does proportion of correct first choices 
           predict average performance (full four minutes data)?") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does average latency to enter the correct side predict proportion of first choices (speed accuracy tradeoff)?
mod<- lm(df$proportion_of_correct_first_choices ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(proportion_of_correct_first_choices)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=30, y=0.8, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average latency to enter the correct side predict 
           proportion of first choices (speed accuracy tradeoff)?") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does average latency to enter the correct side FILTERED predict proportion of first choices (speed accuracy tradeoff)?
mod<- lm(df$proportion_of_correct_first_choices ~ df$average_latency_to_enter_correct_side_filtered_just_correct_choice, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(proportion_of_correct_first_choices)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=30, y=0.8, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side_filtered_just_correct_choice",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average latency to enter the correct side (filtered) predict 
           proportion of first choices (speed accuracy tradeoff)?") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE}
#Does average latency to enter the correct side predict average performance over full 4 minutes data (speed accuracy tradeoff)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_latency_to_enter_correct_side",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Does average latency to enter the correct side predict 
           average performance over full 4 minutes data (speed accuracy tradeoff)?") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does average latency to enter the correct side predict average performance over full 4 minutes data (speed accuracy tradeoff)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_latency_to_enter_correct_side_filtered_just_correct_choice, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_latency_to_enter_correct_side_filtered_just_correct_choice",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Does average latency to enter the correct side (filtered) predict 
           average performance over full 4 minutes data (speed accuracy tradeoff)?") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average latency to enter correct side predict average performance (T30 to T50 data)?
#****************************************************************************** this is the luke set up, use it as a template if needed
mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does average latency to enter correct side predict 
           average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average latency to enter correct side predict average performance (T30 to T50 data)? filtered just correct choice

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_latency_to_enter_correct_side_filtered_just_correct_choice, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_latency_to_enter_correct_side_
filtered_just_correct_choice",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does average latency to enter correct side (filtered)predict 
           average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does Mean of median performance on each ratio (T30 to T50 data) predict proportion of correct first choices?

mod<- lm(df$proportion_of_correct_first_choices ~ df$mean_of_median_performance_on_each_ratio_T30_to_T50_data, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(mean_of_median_performance_on_each_ratio_T30_to_T50_data)) %>% filter(!is.na(proportion_of_correct_first_choices)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_T30_to_T50_data, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "mean_of_median_performance_on_each_ratio_T30_to_T50_data",y="proportion_of_correct_first_choices") +
  ggtitle ("Does Mean of median performance on each ratio 
           (T30 to T50 data) predict proportion of correct first choices?") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does Mean of median performance on each ratio (full 4 minutes) predict proportion of correct first choices?
mod<- lm(df$proportion_of_correct_first_choices ~ df$mean_of_median_performance_on_each_ratio_full_four_minutes_data, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(mean_of_median_performance_on_each_ratio_full_four_minutes_data)) %>% filter(!is.na(proportion_of_correct_first_choices)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_full_four_minutes_data, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "mean_of_median_performance_on_each_ratio_full_four_minutes_data",y="proportion_of_correct_first_choices") +
  ggtitle ("Does Mean of median performance on each ratio 
           (full 4 minutes) predict proportion of correct first choices?") +
  geom_smooth(method = "lm")


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average latency to enter correct side predict mean of median performance on each ratio (mean of median measured in full 4 minutes)?
mod<- lm(df$mean_of_median_performance_on_each_ratio_full_four_minutes_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(mean_of_median_performance_on_each_ratio_full_four_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side, mean_of_median_performance_on_each_ratio_full_four_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=30, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_latency_to_enter_correct_side",y="mean_of_median_performance_on_each_ratio_
       full_four_minutes_data") +
  ggtitle ("Does average latency to enter correct side predict 
           mean of median performance on each ratio (mean of median measured in full 4 minutes)?") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average latency to enter correct side (filtered) predict mean of median performance on each ratio (mean of median measured in full 4 minutes)?
mod<- lm(df$mean_of_median_performance_on_each_ratio_full_four_minutes_data ~ df$average_latency_to_enter_correct_side_filtered_just_correct_choice, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(mean_of_median_performance_on_each_ratio_full_four_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, mean_of_median_performance_on_each_ratio_full_four_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=30, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_latency_to_enter_correct_side_filtered
_just_correct_choice",y="mean_of_median_performance_on_each_ratio_
       full_four_minutes_data") +
  ggtitle ("Does average latency to enter correct side (filtered) predict 
           mean of median performance on each ratio (mean of median measured in full 4 minutes)?") +
  geom_smooth(method = "lm")


```





```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average latency to enter correct side predict mean of median performance on each ratio (mean of median measured in T30 to T50)?
mod<- lm(df$mean_of_median_performance_on_each_ratio_T30_to_T50_data ~ df$average_latency_to_enter_correct_side, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(mean_of_median_performance_on_each_ratio_T30_to_T50_data)) %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side, mean_of_median_performance_on_each_ratio_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_latency_to_enter_correct_side",y="mean_of_median_performance_on_each_ratio_T30_to_T50_data") +
  ggtitle ("Does average latency to enter correct side predict
           mean of median performance on each ratio (mean of median measured in T30 to T50)?") +
  geom_smooth(method = "lm")

#There's originally was no latency 97 (Gavin) because mean_of_medians wasn't calculating if one of the medians was an NA, fixed now (graphs redone as of april 4). 


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average latency to enter correct side (filtered)predict mean of median performance on each ratio (mean of median measured in T30 to T50)?
mod<- lm(df$mean_of_median_performance_on_each_ratio_T30_to_T50_data ~ df$average_latency_to_enter_correct_side_filtered_just_correct_choice, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(mean_of_median_performance_on_each_ratio_T30_to_T50_data)) %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_latency_to_enter_correct_side_filtered_just_correct_choice, mean_of_median_performance_on_each_ratio_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_latency_to_enter_correct_side
       _filtered_just_correct_choice",y="mean_of_median_performance_on_each_ratio_T30_to_T50_data") +
  ggtitle ("Does average latency to enter correct side (filtered)predict
           mean of median performance on each ratio (mean of median measured in T30 to T50)?") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does Mean of median performance on each ratio (full 4 minutes) predict average performance (full 4 minutes data)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$mean_of_median_performance_on_each_ratio_full_four_minutes_data, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(mean_of_median_performance_on_each_ratio_full_four_minutes_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_full_four_minutes_data, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "mean_of_median_performance_on_each_ratio
_full_four_minutes_data",y="average_performance_across_all_9_testing_trials
       _using_full_4_minutes_data") +
  ggtitle ("Does Mean of median performance on each ratio 
           (full 4 minutes) predict average performance (full 4 minutes data)?") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does Mean of median performance on each ratio (T30 to T50 data) predict average performance (T30 to T50 data)?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$mean_of_median_performance_on_each_ratio_T30_to_T50_data, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(mean_of_median_performance_on_each_ratio_T30_to_T50_data)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(mean_of_median_performance_on_each_ratio_T30_to_T50_data, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.6, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "mean_of_median_performance_on_each_ratio_T30_to_T50_data",y="average_performance_across_all_9_testing_trials
       _using_T30_to_T50_data") +
  ggtitle ("Does Mean of median performance on each ratio 
           (T30 to T50 data) predict average performance (T30 to T50 data)?") +
  geom_smooth(method = "lm")


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}

df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)

fit <- aov(average_latency_to_enter_correct_side ~ number_of_medians_above_60_using_full_4_minutes_data, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
kruskalfit<-kruskal.test(average_latency_to_enter_correct_side ~ number_of_medians_above_60_using_full_4_minutes_data, data=df)
p_value_kruskal<- kruskalfit$p.value


#Does number of medians above 60% (full 4 minutes) predict latency to enter correct side?
df$number_of_medians_above_60_using_full_4_minutes_data <-as.character(df$number_of_medians_above_60_using_full_4_minutes_data)
p <- ggplot(df, aes(x=number_of_medians_above_60_using_full_4_minutes_data, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle ('Does number of medians above 60% (full 4 minutes) predict latency to enter correct side?') +
  geom_text(x=2, y=10, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)}, 
                                         p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")
p



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)

fit <- aov(average_latency_to_enter_correct_side_filtered_just_correct_choice ~ number_of_medians_above_60_using_full_4_minutes_data, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]


kruskalfit<-kruskal.test(average_latency_to_enter_correct_side_filtered_just_correct_choice ~ number_of_medians_above_60_using_full_4_minutes_data, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does number of medians above 60% (full 4 minutes) predict latency to enter correct side(filted)?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_full_4_minutes_data, y=average_latency_to_enter_correct_side_filtered_just_correct_choice)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle ('Does number of medians above 60% (full 4 minutes) 
           predict latency to enter correct side (filtered)?') +
  geom_text(x=1, y=80, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)}, 
                                         p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")
p



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)

fit <- aov(average_latency_to_enter_correct_side ~ number_of_medians_above_60_using_T30_to_T50_data, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]


kruskalfit<-kruskal.test(average_latency_to_enter_correct_side ~ number_of_medians_above_60_using_T30_to_T50_data, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does number of medians above 60% (T30 to T50) predict latency to enter correct side?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_T30_to_T50_data, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Does number of medians above 60% (T30 to T50) predict latency to enter correct side?') +
  geom_text(x=2, y=80, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)}, 
                                         p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")
p

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)

fit <- aov(average_latency_to_enter_correct_side_filtered_just_correct_choice ~ number_of_medians_above_60_using_T30_to_T50_data, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]


kruskalfit<-kruskal.test(average_latency_to_enter_correct_side_filtered_just_correct_choice ~ number_of_medians_above_60_using_T30_to_T50_data, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does number of medians above 60% (T30 to T50) predict latency to enter correct side (filtered)?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_T30_to_T50_data, y=average_latency_to_enter_correct_side_filtered_just_correct_choice)) + 
  geom_boxplot()+ stat_n_text() +
  ggtitle('Does number of medians above 60% (T30 to T50) predict 
          latency to enter correct side? (filtered)') +
  geom_text(x=2, y=80, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)}, 
                                         p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")
p

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)

fit <- aov(proportion_of_correct_first_choices ~ number_of_medians_above_60_using_full_4_minutes_data, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]


kruskalfit<-kruskal.test(proportion_of_correct_first_choices ~ number_of_medians_above_60_using_full_4_minutes_data, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does number of medians above 60% (full four minutes) predict proportion of correct first choices?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_full_4_minutes_data, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()+ stat_n_text()
p +  ggtitle ("Does number of medians above 60% (full four minutes) 
             predict proportion of correct first choices?") +
  geom_text(x=1, y=0.8, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
df$number_of_medians_above_60_using_full_4_minutes_data<-as.factor(df$number_of_medians_above_60_using_full_4_minutes_data)
df$number_of_medians_above_60_using_T30_to_T50_data<-as.factor(df$number_of_medians_above_60_using_T30_to_T50_data)
fit <- aov(proportion_of_correct_first_choices ~ number_of_medians_above_60_using_T30_to_T50_data, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]


kruskalfit<-kruskal.test(proportion_of_correct_first_choices ~ number_of_medians_above_60_using_T30_to_T50_data, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does number of medians above 60% (T30 to T50) predict proportion of correct first choices?
p <- ggplot(df, aes(x=number_of_medians_above_60_using_T30_to_T50_data, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does number of medians above 60% (T30 to T50)
              predict proportion of correct first choices?") +
  geom_text(x=2, y=0.8, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```


```{r, echo=FALSE, message=FALSE}
#Does average number of entries predict average performance (full 4 minutes)?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_number_of_entries_full_4_minutes, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_full_4_minutes",y="average_performance_across_all_9_testing_trials
       _using_full_4_minutes_data") +
  ggtitle ("Does average number of entries predict average performance (full 4 minutes)?") +
  geom_smooth(method = "lm")


#note that on march 29 5 points got their average number of entries converted from NA to an actual number which changed the p values a bit. This was because the original script was not continuing over trial in which the number of entries was NA when it was calculating the average, now fixed on march 29 2018

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict average performance (T30 to T50)?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_number_of_entries_full_4_minutes, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_number_of_entries_full_4_minutes",y="average_performance_across_all_9_testing_trials
       _using_T30_to_T50_data") +
  ggtitle ("Does average number of entries predict average performance (T30 to T50)?") +
  geom_smooth(method = "lm")



```


```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predit full 4 minutes?

mod<- lm(df$average_number_of_entries_full_4_minutes ~ df$average_number_of_entries_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_T0_to_T29, average_number_of_entries_full_4_minutes))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=20, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_T0_to_T29",y="average_number_of_entries_full_4_minutes") +
  ggtitle ("Does average number of entries T0-T20 predict average entries (full 4 minutes)?") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predit T30-T50?

mod<- lm(df$average_number_of_entries_T30_to_T50 ~ df$average_number_of_entries_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_number_of_entries_T30_to_T50)) %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_T0_to_T29, average_number_of_entries_T30_to_T50))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=10, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_T0_to_T29",y="average_number_of_entries_full_4_minutes") +
  ggtitle ("Does average number of entries T0-T20 predict average entries (T30_to_T50)?") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predit average_performance_across_all_9_testing_trials_using_full_4_minutes_data?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_number_of_entries_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_T0_to_T29, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_T0_to_T29",y="average_performance_across_all_9_testing_trials_using_full_4_minutes_data") +
  ggtitle ("Does average number of entries T0-T29 predict average performance full 4?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predit average_performance_across_all_9_testing_trials_using_T30_to_T50_data?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_number_of_entries_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_T0_to_T29, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_T0_to_T29",y="average_performance_across_all_9_testing_trials_using_T30_to_T50_data") +
  ggtitle ("Does average number of entries T0-T29 predict average performance T30_to_T50?") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predit proportion of ccorrect first choies?

mod<- lm(df$proportion_of_correct_first_choices ~ df$average_number_of_entries_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_T0_to_T29, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_T0_to_T29",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average number of entries T0-T29 predict proportion of correct first choices") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predit average latency to enter correct side?

mod<- lm(df$average_latency_to_enter_correct_side ~ df$average_number_of_entries_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_number_of_entries_T0_to_T29, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_T0_to_T29",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does average number of entries T0-T29 predict average latency to enter correct side") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does prop time thigmo T0-T29 predit average_performance_across_all_9_testing_trials_using_full_4_minutes_data?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_prop_time_thigmo_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(average_prop_time_thigmo_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_thigmo_T0_to_T29, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_thigmo_T0_to_T29",y="average_performance_across_all_9_testing_trials_using_full_4_minutes_data") +
  ggtitle ("Does prop time thigmo T0-T29 predict average performance full 4?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does prop time thigmo T0-T29 predit average_performance_across_all_9_testing_trials_using_T30_to_T50_data?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_prop_time_thigmo_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_prop_time_thigmo_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_thigmo_T0_to_T29, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_thigmo_T0_to_T29",y="average_performance_across_all_9_testing_trials_using_T30_to_T50_data") +
  ggtitle ("Does prop time thigmo T0-T29 predict average performance T30_to_T50?") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does prop time thigmo T0-T29 predit proportion of ccorrect first choies?

mod<- lm(df$proportion_of_correct_first_choices ~ df$average_prop_time_thigmo_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_prop_time_thigmo_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_thigmo_T0_to_T29, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_thigmo_T0_to_T29",y="proportion_of_correct_first_choices") +
  ggtitle ("Does prop time thigmo T0-T29 predict proportion of correct first choices") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does prop time thigmo T0-T29 predit average latency to enter correct side?

mod<- lm(df$average_latency_to_enter_correct_side ~ df$average_prop_time_thigmo_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_prop_time_thigmo_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_thigmo_T0_to_T29, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=100, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_thigmo_T0_to_T29",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does prop time thigmo T0-T29 predict average latency to enter correct side") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Doesprop_time mirror 0-29 predit average_performance_across_all_9_testing_trials_using_full_4_minutes_data?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_prop_time_mirror_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_mirror_T0_to_T29, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_mirror_T0_to_T29",y="average_performance_across_all_9_testing_trials_using_full_4_minutes_data") +
  ggtitle ("Does prop_time mirror 0-29 predict average performance full 4?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does prop_time mirror 0-29 predit average_performance_across_all_9_testing_trials_using_T30_to_T50_data?

mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_prop_time_mirror_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_mirror_T0_to_T29, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_mirror_T0_to_T29",y="average_performance_across_all_9_testing_trials_using_T30_to_T50_data") +
  ggtitle ("Does prop_time mirror 0-29 predict average performance T30_to_T50?") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does prop_time mirror 0-29 predit proportion of ccorrect first choies?

mod<- lm(df$proportion_of_correct_first_choices ~ df$average_prop_time_mirror_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_mirror_T0_to_T29, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_mirror_T0_to_T29",y="proportion_of_correct_first_choices") +
  ggtitle ("Does prop_time mirror 0-29 predict proportion of correct first choices") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does prop_time mirror 0-29 predit average latency to enter correct side?

mod<- lm(df$average_latency_to_enter_correct_side ~ df$average_prop_time_mirror_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_mirror_T0_to_T29, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=10, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_mirror_T0_to_T29",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does prop_time mirror T0-T29 predict average latency to enter correct side") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does prop time mirror predict entries t0-29?

mod<- lm(df$average_number_of_entries_T0_to_T29 ~ df$average_prop_time_mirror_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_mirror_T0_to_T29, average_number_of_entries_T0_to_T29))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.2, y=10, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_mirror_T0_to_T29",y="average_number_of_entries_T0_to_T29") +
  ggtitle ("Does average number of entries T0-T29 predict prop time mirror") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE}
#Does prop time thigmo predict entries t0-29?

mod<- lm(df$average_number_of_entries_T0_to_T29 ~ df$average_prop_time_thigmo_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_number_of_entries_T0_to_T29)) %>% filter(!is.na(average_prop_time_thigmo_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_thigmo_T0_to_T29, average_number_of_entries_T0_to_T29))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.4, y=10, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_thigmo_T0_to_T29",y="average_number_of_entries_T0_to_T29") +
  ggtitle ("Does prop time thigmo predict average number of entries T0-T29") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE}
#Does prop time thigmo predict prop time mirror?

mod<- lm(df$average_prop_time_mirror_T0_to_T29 ~ df$average_prop_time_thigmo_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% filter(!is.na(average_prop_time_thigmo_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_thigmo_T0_to_T29, average_prop_time_mirror_T0_to_T29))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=0.3, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_thigmo_T0_to_T29",y="average_prop_time_mirror_T0_to_T29") +
  ggtitle ("Does prop time thigmo predict prop time mirror") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE}
#Does average number of entries T0-29 predict average latency to enter correct side?

mod<- lm(df$average_latency_to_enter_correct_side ~ df$average_prop_time_mirror_T0_to_T29, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_prop_time_mirror_T0_to_T29)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(average_prop_time_mirror_T0_to_T29, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_prop_time_mirror_T0_to_T29",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does average number of entries T0-T29 predict average latency to enter correct side") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict average performance (T30 to T50)? separated by sex
mod<-lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_number_of_entries_full_4_minutes * df$sex)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]


p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_performance_across_all_9_testing_trials_using_T30_to_T50_data, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p (interaction)= {round(p_value,4)} 
  n = {number}"), size = 6, color = "black") + 
  labs(x= "average_number_of_entries_full_4_minutes",y="average_performance_across_all_9_testing_trials
       _using_T30_to_T50_data") +
  ggtitle ("Does average number of entries predict average performance (T30 to T50)?") +
  geom_smooth(method = "lm")



```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict proportion of correct choices?
mod<- lm(df$proportion_of_correct_first_choices ~ df$average_number_of_entries_full_4_minutes, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_number_of_entries_full_4_minutes",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average number of entries predict proportion of correct choices?") +
  geom_smooth(method = "lm")



```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict proportion of correct choices?separated by sex
mod<-lm(df$proportion_of_correct_first_choices ~ df$average_number_of_entries_full_4_minutes * df$sex)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]


p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, proportion_of_correct_first_choices, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p (interaction)= {round(p_value,4)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "average_number_of_entries_full_4_minutes",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average number of entries predict proportion of correct choices?") +
  geom_smooth(method = "lm")



```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict average latency to enter correct side?
mod<- lm(df$average_latency_to_enter_correct_side ~ df$average_number_of_entries_full_4_minutes, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_full_4_minutes",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does average number of entries predict average latency to enter correct side?") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict average latency to enter correct side (filtered)?
mod<- lm(df$average_latency_to_enter_correct_side_filtered_just_correct_choice ~ df$average_number_of_entries_full_4_minutes, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_latency_to_enter_correct_side_filtered_just_correct_choice))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_full_4_minutes",y="average_latency_to_enter_correct_side_filtered_just_correct_choice") +
  ggtitle ("Does average number of entries predict 
           average latency to enter correct side?(filtered)") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict average latency to enter correct side?separated by sex
mod<-lm(df$average_latency_to_enter_correct_side ~ df$average_number_of_entries_full_4_minutes * df$sex)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_latency_to_enter_correct_side, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p (interaction)= {round(p_value,4)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_full_4_minutes",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does average number of entries predict average latency to enter correct side?") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average number of entries predict average latency to enter correct side? (filtered)separated by sex
mod<-lm(df$average_latency_to_enter_correct_side_filtered_just_correct_choice ~ df$average_number_of_entries_full_4_minutes * df$sex)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(average_number_of_entries_full_4_minutes, average_latency_to_enter_correct_side_filtered_just_correct_choice, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.2, label= glue::glue("p (interaction)= {round(p_value,4)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_number_of_entries_full_4_minutes",y="average_latency_to_enter_correct_side_filtered_just_correct_choice") +
  ggtitle ("Does average number of entries predict average latency to enter correct side? (filtered)") +
  geom_smooth(method = "lm")


```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict average performance (full 4 minutes)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_reaction_time, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=20, y=0.1, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_performance_across_all_9_testing_trials
       _using_full_4_minutes_data") +
  ggtitle ("Does average reaction time predict 
           average performance (full 4 minutes)?") +
  geom_smooth(method = "lm")



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict average performance (T30 to T50)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)


number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_reaction_time, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does average reaction time predict average performance (T30 to T50)?") +
  geom_smooth(method = "lm")


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict average performance (T30 to T50)?separated by sex
mod<-lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$average_reaction_time * df$sex)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(average_reaction_time, average_performance_across_all_9_testing_trials_using_T30_to_T50_data, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=25, y=0.5, label= glue::glue("p (interaction)= {round(p_value,4)},
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does average reaction time predict average performance (T30 to T50)?") +
  geom_smooth(method = "lm")


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict proportion of correct choices?
mod<- lm(df$proportion_of_correct_first_choices ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_reaction_time, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average reaction time predict proportion of correct choices?") +
  geom_smooth(method = "lm")



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict proportion of correct choices?separated by sex
mod<-lm(df$proportion_of_correct_first_choices ~ df$average_reaction_time * df$sex)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]


p <- ggplot(df, aes(average_reaction_time, proportion_of_correct_first_choices, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.2, label= glue::glue("p (interaction)= {round(p_value,4)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="proportion_of_correct_first_choices") +
  ggtitle ("Does average reaction time predict proportion of correct choices?") +
  geom_smooth(method = "lm")



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict latency to enter correct side?
mod<- lm(df$average_latency_to_enter_correct_side ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_reaction_time, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does average reaction time predict latency to enter correct side?") +
  geom_smooth(method = "lm")

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict latency to enter correct side (filtered)?
mod<- lm(df$average_latency_to_enter_correct_side_filtered_just_correct_choice ~ df$average_reaction_time, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(average_reaction_time, average_latency_to_enter_correct_side_filtered_just_correct_choice))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_latency_to_enter_correct_side(filtered)") +
  ggtitle ("Does average reaction time predict latency to enter correct side? (filtered)") +
  geom_smooth(method = "lm")

```





```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict latency to enter correct side?separated by sex
mod<-lm(df$average_latency_to_enter_correct_side ~ df$average_reaction_time * df$sex)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(average_reaction_time, average_latency_to_enter_correct_side, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=10, label= glue::glue("p (interaction)= {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does average reaction time predict latency to enter correct side?") +
  geom_smooth(method = "lm")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does average reaction time predict latency to enter correct side (filtered)?separated by sex
mod<-lm(df$average_latency_to_enter_correct_side_filtered_just_correct_choice ~ df$average_reaction_time * df$sex)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(average_reaction_time)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(average_reaction_time, average_latency_to_enter_correct_side_filtered_just_correct_choice, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=10, y=10, label= glue::glue("p (interaction)= {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "average_reaction_time",y="average_latency_to_enter_correct_side_filtered_just_correct_choice") +
  ggtitle ("Does average reaction time predict latency to enter correct side? (filtered)") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict average performance over the full 4 minutes?
#This is a wilcoxon rank sum test

test<-t.test(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data~ df$sex)
wilcox_test$estimate
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0.2, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does sex predict average performance over the full 4 minutes?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict average performance over T30 to T50?
test<-t.test(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data~df$sex)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does sex predict average performance over T30 to T50?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict average latency to enter correct zone?
test<-t.test(df$average_latency_to_enter_correct_side~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist

wilcox_test<-wilcox.test(df$average_latency_to_enter_correct_side~df$sex)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does sex predict average latency to enter correct zone?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict average latency to enter correct zone?(filtered)
test<-t.test(df$average_latency_to_enter_correct_side_filtered_just_correct_choice~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist

wilcox_test<-wilcox.test(df$average_latency_to_enter_correct_side_filtered_just_correct_choice~df$sex)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=average_latency_to_enter_correct_side_filtered_just_correct_choice)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does sex predict average latency to enter correct zone?(filtered)")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict proportion of correct choices?
test<-t.test(df$proportion_of_correct_first_choices~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist

wilcox_test<-wilcox.test(df$proportion_of_correct_first_choices~df$sex)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does sex predict proportion of correct choices?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict average number of entries?
test<-t.test(df$average_number_of_entries_full_4_minutes~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist

wilcox_test<-wilcox.test(df$average_number_of_entries_full_4_minutes~df$sex)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=average_number_of_entries_full_4_minutes)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=110, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black") 
p +  ggtitle ("Does sex predict average number of entries?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does sex predict average reaction time?
test<-t.test(df$average_reaction_time~df$sex)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist

wilcox_test<-wilcox.test(df$average_reaction_time~df$sex)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=sex, y=average_reaction_time)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does sex predict average reaction time?")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average performance (full 4 minutes)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_full_4_minutes_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Does size/age predict average performance (full 4 minutes)? SEXES COMBINED") +
  geom_smooth(method = "lm")


```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average perfomrance (full 4 minutes)? by sex
mod<-lm(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_full_4_minutes_data, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_full_4_minutes_data") +
  ggtitle ("Does size/age predict average performance (full 4 minutes)?separated by sex") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average performance(T30 to T50)?
mod<- lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_T30_to_T50_data))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1700, y=0.3, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does size/age predict average performance(T30 to T50)?SEXES COMBINED") +
  geom_smooth(method = "lm")


```




```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average performance(T30 to T50)? by sex
mod<-lm(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]


p <- ggplot(df, aes(standard_length, average_performance_across_all_9_testing_trials_using_T30_to_T50_data, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_performance_across_all_9_testing_trials_
       using_T30_to_T50_data") +
  ggtitle ("Does size/age predict average performance(T30 to T50)? separated by sex") +
  geom_smooth(method = "lm")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict proportion of correct choices?
mod<- lm(df$proportion_of_correct_first_choices ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(standard_length, proportion_of_correct_first_choices))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1700, y=0.1, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="proportion_of_correct_first_choices") +
  ggtitle ("Does size/age predict proportion of correct choices?SEXES COMBINED") +
  geom_smooth(method = "lm")



```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict proportion of correct choices? by sex

mod<-lm(df$proportion_of_correct_first_choices ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(proportion_of_correct_first_choices)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(standard_length, proportion_of_correct_first_choices, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") + 
  labs(x= "standard_length",y="proportion_of_correct_first_choices") +
  ggtitle ("Does size/age predict proportion of correct choices?") +
  geom_smooth(method = "lm")


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average latency to enter correct side?
mod<- lm(df$average_latency_to_enter_correct_side ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(standard_length, average_latency_to_enter_correct_side))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1800, y=75, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "standard_length",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does size/age predict average latency to enter correct side? SEXES COMBINED") +
  geom_smooth(method = "lm")



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average latency to enter correct side (filtered)?
mod<- lm(df$average_latency_to_enter_correct_side_filtered_just_correct_choice ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(standard_length, average_latency_to_enter_correct_side_filtered_just_correct_choice))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1800, y=75, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "standard_length",y="average_latency_to_enter_correct_side_filtered_just_correct_choice") +
  ggtitle ("Does size/age predict average latency to enter correct side (filtered)? SEXES COMBINED") +
  geom_smooth(method = "lm")



```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average latency to enter correct side? by sex
mod<-lm(df$average_latency_to_enter_correct_side ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(standard_length, average_latency_to_enter_correct_side, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=20, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_latency_to_enter_correct_side") +
  ggtitle ("Does size/age predict average latency to enter correct side?") +
  geom_smooth(method = "lm")


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average latency to enter correct side _filtered)? by sex
mod<-lm(df$average_latency_to_enter_correct_side_filtered_just_correct_choice ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(average_latency_to_enter_correct_side_filtered_just_correct_choice)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(standard_length, average_latency_to_enter_correct_side_filtered_just_correct_choice, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=20, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_latency_to_enter_correct_side_filtered_just_correct_choice") +
  ggtitle ("Does size/age predict average latency to enter correct side? (filtered)") +
  geom_smooth(method = "lm")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average number of entries?
mod<- lm(df$average_number_of_entries_full_4_minutes ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist

p <- ggplot(df, aes(standard_length, average_number_of_entries_full_4_minutes))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", 1800, y=100, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_number_of_entries_full_4_minutes") +
  ggtitle ("Does size/age predict average number of entries?SEXES COMBINED") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict average number of entries? by sex
mod<-lm(df$average_number_of_entries_full_4_minutes ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(average_number_of_entries_full_4_minutes)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(standard_length, average_number_of_entries_full_4_minutes, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_number_of_entries_full_4_minutes") +
  ggtitle ("Does size/age predict average number of entries? by sex") +
  geom_smooth(method = "lm")


```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict reaction time?
mod<- lm(df$average_reaction_time ~ df$standard_length, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(average_reaction_time)) %>% filter(!is.na(standard_length)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(standard_length, average_reaction_time))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1800, y=30, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "standard_length",y="average_reaction_time") +
  ggtitle ("Does size/age predict reaction time? SEXES COMBINED") +
  geom_smooth(method = "lm")


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Does size/age predict reaction time? by sex
mod<-lm(df$average_reaction_time ~ df$standard_length * df$sex)

number <- df %>% filter(!is.na(average_reaction_time)) %>% filter(!is.na(standard_length)) %>% nrow
p_value<- coef(summary(mod))%>%as.list()
p_value<-p_value[[16]]

p <- ggplot(df, aes(standard_length, average_reaction_time, color = sex))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=1600, y=0.2, label= glue::glue("p (interaction) = {round(p_value,4)}
       n = {number}"), size = 6, color = "black") +
  labs(x= "standard_length",y="average_reaction_time") +
  ggtitle ("Does size/age predict reaction time? by sex") +
  geom_smooth(method = "lm")


```






```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(average_performance_across_all_9_testing_trials_using_full_4_minutes_data ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict average performance over the full 4 minutes?
p <- ggplot(df, aes(x=order, y=average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict average performance over the full 4 minutes?")+
  geom_text(x=3, y=0.2, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(average_performance_across_all_9_testing_trials_using_T30_to_T50_data ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict performance over T30 to T50?
p <- ggplot(df, aes(x=order, y=average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict performance over T30 to T50?")+
  geom_text(x=3, y=0.2, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(average_latency_to_enter_correct_side ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(average_latency_to_enter_correct_side ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict average latency to enter correct side?
p <- ggplot(df, aes(x=order, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict average latency to enter correct side?")+
  geom_text(x=3, y=0.2, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(average_latency_to_enter_correct_side_filtered_just_correct_choice ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(average_latency_to_enter_correct_side_filtered_just_correct_choice ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict average latency to enter correct side(filtered)?
p <- ggplot(df, aes(x=order, y=average_latency_to_enter_correct_side_filtered_just_correct_choice)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict average latency to enter correct side?(filtered)")+
  geom_text(x=3, y=0.2, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(proportion_of_correct_first_choices ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(proportion_of_correct_first_choices ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict proportion of correct choices?
p <- ggplot(df, aes(x=order, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict proportion of correct choices?")+
  geom_text(x=3, y=0.2, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(average_number_of_entries_full_4_minutes ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(average_number_of_entries_full_4_minutes ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict average number of entries?
p <- ggplot(df, aes(x=order, y=average_number_of_entries_full_4_minutes)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict average number of entries?")+
  geom_text(x=3, y=120, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                          p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
fit <- aov(average_reaction_time ~ order, data=df) 
p_value_ANOVA<- summary(fit)[[1]][["Pr(>F)"]][[1]]
df$order<-as.factor(df$order)

kruskalfit<-kruskal.test(average_reaction_time ~ order, data=df)
p_value_kruskal<- kruskalfit$p.value

#Does order predict average reaction time?
p <- ggplot(df, aes(x=order, y=average_reaction_time)) + 
  geom_boxplot()+ stat_n_text() 
p +  ggtitle ("Does order predict average reaction time?") +
  geom_text(x=3, y=30, label= glue::glue("p (ANOVA) = {round(p_value_ANOVA,4)},
                                         p(Kruskal) = {round(p_value_kruskal,4)}"), size = 6, color = "black")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average performance over full_4_minutes?

test<-t.test(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_performance_across_all_9_testing_trials_using_full_4_minutes_data~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_performance_across_all_9_testing_trials_using_full_4_minutes_data)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0.4, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average performance over full_4_minutes?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average performance over T30 to T50?

test<-t.test(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_performance_across_all_9_testing_trials_using_T30_to_T50_data~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_performance_across_all_9_testing_trials_using_T30_to_T50_data)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average performance over T30 to T50?")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict proportion_of_correct_first_choice?

test<-t.test(df$proportion_of_correct_first_choices~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$proportion_of_correct_first_choices~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=proportion_of_correct_first_choices)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0.4, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict proportion_of_correct_first_choices?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_latency_to_enter_correct_side?

test<-t.test(df$average_latency_to_enter_correct_side~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_latency_to_enter_correct_side~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_latency_to_enter_correct_side)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0.4, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_latency_to_enter_correct_side?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_number_of_entries_full_4_minutes?

test<-t.test(df$average_number_of_entries_full_4_minutes~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_number_of_entries_full_4_minutes~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_number_of_entries_full_4_minutes)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=20, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_number_of_entries_full_4_minutes?")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_number_of_entries_T0_to_T29?

test<-t.test(df$average_number_of_entries_T0_to_T29~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_number_of_entries_T0_to_T29~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_number_of_entries_T0_to_T29)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=10, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_number_of_entries_T0_to_T29?")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_prop_time_thigmo_T0_to_T29?

test<-t.test(df$average_prop_time_thigmo_T0_to_T29~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_prop_time_thigmo_T0_to_T29~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_prop_time_thigmo_T0_to_T29)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0.6, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_prop_time_thigmo_T0_to_T29?")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_prop_time_mirror_T0_to_T29?

test<-t.test(df$average_prop_time_mirror_T0_to_T29~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_prop_time_mirror_T0_to_T29~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_prop_time_mirror_T0_to_T29)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=0.6, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_prop_time_mirror_T0_to_T29?")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_number_of_entries_full_4_minutes?
df$did_fish_have_a_median_above_60<-as.factor(df$did_fish_have_a_median_above_60)

test<-t.test(df$average_number_of_entries_full_4_minutes~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_number_of_entries_full_4_minutes~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_number_of_entries_full_4_minutes)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=20, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_number_of_entries_full_4_minutes?")
p

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_number_of_entries_T30_to_T50?
df$did_fish_have_a_median_above_60<-as.factor(df$did_fish_have_a_median_above_60)

test<-t.test(df$average_number_of_entries_T30_to_T50~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_number_of_entries_T30_to_T50~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_number_of_entries_T30_to_T50)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=10, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_number_of_entries_T30_to_T50?")
p

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict aaverage_reaction_time?
df$did_fish_have_a_median_above_60<-as.factor(df$did_fish_have_a_median_above_60)

test<-t.test(df$average_reaction_time~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_reaction_time~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_reaction_time)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=10, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_reaction_time?")
p

```




```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Does learning a median predict average_reaction_time?
df$did_fish_have_a_median_above_60<-as.factor(df$did_fish_have_a_median_above_60)

test<-t.test(df$average_number_of_entries_full_4_minutes~df$did_fish_have_a_median_above_60)
p_value_t<- test %>% broom::tidy() %>% select(p.value) %>% unlist
wilcox_test<-wilcox.test(df$average_number_of_entries_full_4_minutes~df$did_fish_have_a_median_above_60)
p_value_wilcox<-wilcox_test$p.value

p <- ggplot(df, aes(x=did_fish_have_a_median_above_60, y=average_number_of_entries_full_4_minutes)) + 
  geom_boxplot()+ stat_n_text() +
  geom_text(x=1, y=10, label= glue::glue("p (t-test)= {round(p_value_t,4)}, 
                                          p(wilcox) = {round(p_value_wilcox,4)}"), size = 6, color = "black")
p +  ggtitle ("Does learning 1+ median predict average_number of entries full four minutes?")
p

```




TEMPLATE AGAIN

mod<- lm(df$XXX ~ df$XXX, na.rm = TRUE)
summary(mod)

number <- df %>% filter(!is.na(XXX)) %>% filter(!is.na(XXX)) %>% nrow
p_value <- mod %>% broom::tidy() %>% filter(term != "(Intercept)") %>% select(p.value) %>% unlist
r_squared <- mod %>% broom::glance() %>% select(r.squared) %>% unlist


p <- ggplot(df, aes(XXX, XXX))
p + geom_point(size = 4) + 
  theme(text = element_text(size=10)) + 
  annotate("text", x=50, y=0.5, label= glue::glue("p = {round(p_value,4)}, R-squared:  {round(r_squared,3)}
        n = {number}"), size = 6, color = "black") + 
  labs(x= "XXX",y="XXX") +
  ggtitle ("XXX") +
  geom_smooth(method = "lm")



4. See how consistent individuals are across trials within the same individuals (so will have an average repeatibility score?)
Performance over the full 4 minutes
Performance over T30 to T50
Which side was chosen first


 Here's the column names coming from df.sum:

"fish_name"                                                                                                        
  [2] "sex"                                                                                                              
  [3] "standard_length"                                                                                                  
  [4] "order"   
  
------------------------------------------------------------------------
  
[149] "average_number_of_entries_full_4_minutes"                                                                                        
[150] "average_reaction_time"                                                                                            
[151] "average_performance_across_all_9_testing_trials_using_full_4_minutes_data"                                        
[152] "average_performance_across_all_9_testing_trials_using_T30_to_T50_data"                                            
[153] "total_number_of_testing_trials_using_full_4_minutes_data"                                                         
[154] "total_number_of_testing_trials_using_T30_to_T50_data"                                                             
[155] "number_of_trials_on_0.50_ratio_using_full_4_minutes_data"                                                         
[156] "number_of_trials_on_0.67_ratio_using_full_4_minutes_data"                                                         
[157] "number_of_trials_on_0.75_ratio_using_full_4_minutes_data"                                                         
[158] "number_of_trials_on_0.50_ratio_using_T30_to_T50_data"                                                             
[159] "number_of_trials_on_0.67_ratio_using_T30_to_T50_data"                                                             
[160] "number_of_trials_on_0.75_ratio_using_T30_to_T50_data"                                                             
[161] "median_performance_on_0.50_ratio_using_full_4_minutes_data"                                                       
[162] "median_performance_on_0.67_ratio_using_full_4_minutes_data"                                                       
[163] "median_performance_on_0.75_ratio_using_full_4_minutes_data"                                                       
[164] "median_performance_on_0.50_ratio_using_T30_to_T50_data"                                                           
[165] "median_performance_on_0.67_ratio_using_T30_to_T50_data"                                                           
[166] "median_performance_on_0.75_ratio_using_T30_to_T50_data"                                                           
[167] "number_of_medians_above_60_using_full_4_minutes_data"                                                             
[168] "number_of_medians_above_60_using_T30_to_T50_data"                                                                 
[169] "shapiro_wilk_test_p_value_using_full_4_minutes_data"                                                              
[170] "was_average_performance_significantly_different_from_0.5_full_4_minutes_p_value_of_either_t_test_or_wilcox"       
[171] "shapiro_wilk_test_p_value_using_T30_to_T50_data"                                                                  
[172] "was_average_performance_significantly_different_from_0.5_T30_to_T50_p_value_of_either_t_test_or_wilcox"           
[173] "learning_category_according_to_etheredge_T30_to_T50"                                                              
[174] "learning_category_according_to_etheredge_full_4_minutes"                                                          
[175] "average_latency_to_enter_correct_side"                                                                            
[176] "average_latency_to_enter_incorrect_side"                                                                          
[177] "proportion_of_correct_first_choices"                                                                              
[178] "number_of_trials_in_a_row_greater_than_60_percent_full_4_minutes"                                                 
[179] "number_of_trials_in_a_row_greater_than_60_percent_T30_to_T50"                                                     
[180] "number_of_trials_in_a_row_correct_choice_first"                                                                   
[181] "mean_of_median_performance_on_each_ratio_full_four_minutes_data"                                                  
[182] "mean_of_median_performance_on_each_ratio_T30_to_T50_data" 

------------------------------------------------------------------------

 [5] "Trial_9_1_correctside"                                                                                            
  [6] "Trial_9_1_ratio"                                                                                                  
  [7] "Trial_9_1_total_entries"                                                                                          
  [8] "Trial_9_1_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens" 
  [9] "Trial_9_1_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"     
 [10] "Trial_9_1_was_performance_over_full_4_minutes_greater_than_60_percent"                                            
 [11] "Trial_9_1_was_performance_T30_to_T50_greater_than_60_percent"                                                     
 [12] "Trial_9_1_reaction_time"                                                                                          
 [13] "Trial_9_1_latency_to_enter_correct_side"                                                                          
 [14] "Trial_9_1_latency_to_enter_incorrect_side"                                                                        
 [15] "Trial_9_1_screen_entered_first"                                                                                   
 [16] "Trial_9_1_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                           
 [17] "Trial_9_1_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                         
 [18] "Trial_9_1_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                               
 [19] "Trial_9_1_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                             
 [20] "Trial_9_3_correctside"                                                                                            
 [21] "Trial_9_3_ratio"                                                                                                  
 [22] "Trial_9_3_total_entries"                                                                                          
 [23] "Trial_9_3_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens" 
 [24] "Trial_9_3_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"     
 [25] "Trial_9_3_was_performance_over_full_4_minutes_greater_than_60_percent"                                            
 [26] "Trial_9_3_was_performance_T30_to_T50_greater_than_60_percent"                                                     
 [27] "Trial_9_3_reaction_time"                                                                                          
 [28] "Trial_9_3_latency_to_enter_correct_side"                                                                          
 [29] "Trial_9_3_latency_to_enter_incorrect_side"                                                                        
 [30] "Trial_9_3_screen_entered_first"                                                                                   
 [31] "Trial_9_3_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                           
 [32] "Trial_9_3_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                         
 [33] "Trial_9_3_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                               
 [34] "Trial_9_3_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                             
 [35] "Trial_9_5_correctside"                                                                                            
 [36] "Trial_9_5_ratio"                                                                                                  
 [37] "Trial_9_5_total_entries"                                                                                          
 [38] "Trial_9_5_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens" 
 [39] "Trial_9_5_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"     
 [40] "Trial_9_5_was_performance_over_full_4_minutes_greater_than_60_percent"                                            
 [41] "Trial_9_5_was_performance_T30_to_T50_greater_than_60_percent"                                                     
 [42] "Trial_9_5_reaction_time"                                                                                          
 [43] "Trial_9_5_latency_to_enter_correct_side"                                                                          
 [44] "Trial_9_5_latency_to_enter_incorrect_side"                                                                        
 [45] "Trial_9_5_screen_entered_first"                                                                                   
 [46] "Trial_9_5_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                           
 [47] "Trial_9_5_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                         
 [48] "Trial_9_5_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                               
 [49] "Trial_9_5_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                             
 [50] "Trial_10_1_correctside"                                                                                           
 [51] "Trial_10_1_ratio"                                                                                                 
 [52] "Trial_10_1_total_entries"                                                                                         
 [53] "Trial_10_1_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [54] "Trial_10_1_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
 [55] "Trial_10_1_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
 [56] "Trial_10_1_was_performance_T30_to_T50_greater_than_60_percent"                                                    
 [57] "Trial_10_1_reaction_time"                                                                                         
 [58] "Trial_10_1_latency_to_enter_correct_side"                                                                         
 [59] "Trial_10_1_latency_to_enter_incorrect_side"                                                                       
 [60] "Trial_10_1_screen_entered_first"                                                                                  
 [61] "Trial_10_1_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
 [62] "Trial_10_1_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
 [63] "Trial_10_1_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
 [64] "Trial_10_1_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
 [65] "Trial_10_3_correctside"                                                                                           
 [66] "Trial_10_3_ratio"                                                                                                 
 [67] "Trial_10_3_total_entries"                                                                                         
 [68] "Trial_10_3_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [69] "Trial_10_3_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
 [70] "Trial_10_3_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
 [71] "Trial_10_3_was_performance_T30_to_T50_greater_than_60_percent"                                                    
 [72] "Trial_10_3_reaction_time"                                                                                         
 [73] "Trial_10_3_latency_to_enter_correct_side"                                                                         
 [74] "Trial_10_3_latency_to_enter_incorrect_side"                                                                       
 [75] "Trial_10_3_screen_entered_first"                                                                                  
 [76] "Trial_10_3_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
 [77] "Trial_10_3_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
 [78] "Trial_10_3_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
 [79] "Trial_10_3_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
 [80] "Trial_10_5_correctside"                                                                                           
 [81] "Trial_10_5_ratio"                                                                                                 
 [82] "Trial_10_5_total_entries"                                                                                         
 [83] "Trial_10_5_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [84] "Trial_10_5_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
 [85] "Trial_10_5_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
 [86] "Trial_10_5_was_performance_T30_to_T50_greater_than_60_percent"                                                    
 [87] "Trial_10_5_reaction_time"                                                                                         
 [88] "Trial_10_5_latency_to_enter_correct_side"                                                                         
 [89] "Trial_10_5_latency_to_enter_incorrect_side"                                                                       
 [90] "Trial_10_5_screen_entered_first"                                                                                  
 [91] "Trial_10_5_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
 [92] "Trial_10_5_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
 [93] "Trial_10_5_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
 [94] "Trial_10_5_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
 [95] "Trial_11_1_correctside"                                                                                           
 [96] "Trial_11_1_ratio"                                                                                                 
 [97] "Trial_11_1_total_entries"                                                                                         
 [98] "Trial_11_1_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
 [99] "Trial_11_1_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
[100] "Trial_11_1_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
[101] "Trial_11_1_was_performance_T30_to_T50_greater_than_60_percent"                                                    
[102] "Trial_11_1_reaction_time"                                                                                         
[103] "Trial_11_1_latency_to_enter_correct_side"                                                                         
[104] "Trial_11_1_latency_to_enter_incorrect_side"                                                                       
[105] "Trial_11_1_screen_entered_first"                                                                                  
[106] "Trial_11_1_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
[107] "Trial_11_1_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
[108] "Trial_11_1_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
[109] "Trial_11_1_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
[110] "Trial_11_3_correctside"                                                                                           
[111] "Trial_11_3_ratio"                                                                                                 
[112] "Trial_11_3_total_entries"                                                                                         
[113] "Trial_11_3_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
[114] "Trial_11_3_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
[115] "Trial_11_3_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
[116] "Trial_11_3_was_performance_T30_to_T50_greater_than_60_percent"                                                    
[117] "Trial_11_3_reaction_time"                                                                                         
[118] "Trial_11_3_latency_to_enter_correct_side"                                                                         
[119] "Trial_11_3_latency_to_enter_incorrect_side"                                                                       
[120] "Trial_11_3_screen_entered_first"                                                                                  
[121] "Trial_11_3_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
[122] "Trial_11_3_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
[123] "Trial_11_3_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
[124] "Trial_11_3_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
[125] "Trial_11_5_correctside"                                                                                           
[126] "Trial_11_5_ratio"                                                                                                 
[127] "Trial_11_5_total_entries"                                                                                         
[128] "Trial_11_5_performance_over_full_4_minutes_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"
[129] "Trial_11_5_performance_over_T30_to_T50_ie_correct_screen_proportion_divided_by_sum_proportion_at_both_screens"    
[130] "Trial_11_5_was_performance_over_full_4_minutes_greater_than_60_percent"                                           
[131] "Trial_11_5_was_performance_T30_to_T50_greater_than_60_percent"                                                    
[132] "Trial_11_5_reaction_time"                                                                                         
[133] "Trial_11_5_latency_to_enter_correct_side"                                                                         
[134] "Trial_11_5_latency_to_enter_incorrect_side"                                                                       
[135] "Trial_11_5_screen_entered_first"                                                                                  
[136] "Trial_11_5_time_spent_in_correct_screen_full_4_minutes_absolute_seconds"                                          
[137] "Trial_11_5_time_spent_in_incorrect_screen_full_4_minutes_absolute_seconds"                                        
[138] "Trial_11_5_time_spent_in_correct_screen_T30_to_T50_absolute_seconds"                                              
[139] "Trial_11_5_time_spent_in_incorrect_screen_T30_to_T50_absolute_seconds"                                            
[140] "Trial_9_1_was_fish_in_correct_screen_at_start"                                                                    
[141] "Trial_9_3_was_fish_in_correct_screen_at_start"                                                                    
[142] "Trial_9_5_was_fish_in_correct_screen_at_start"                                                                    
[143] "Trial_10_1_was_fish_in_correct_screen_at_start"                                                                   
[144] "Trial_10_3_was_fish_in_correct_screen_at_start"                                                                   
[145] "Trial_10_5_was_fish_in_correct_screen_at_start"                                                                   
[146] "Trial_11_1_was_fish_in_correct_screen_at_start"                                                                   
[147] "Trial_11_3_was_fish_in_correct_screen_at_start"                                                                   
[148] "Trial_11_5_was_fish_in_correct_screen_at_start"                             

```{r}

```





